---
title: "Larval Project Portion of Compendium"
output:
  pdf_document:
    fig_width: 6
    fig_height: 4
date: "2026-02-05"
---

```{r setup, include=FALSE}

#clear environment first
rm(list=ls())

year= substr(Sys.Date(),1,4)
#knitr::opts_knit$set(root.dir = paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/"))
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, fig.align='center')


```


```{r Data Import, include=FALSE}
#Import all packages, CTD data, and land data

local({r <- getOption("repos")
       r["CRAN"] <- "https://cran.r-project.org" 
       options(repos=r)
})

#Packages
library(ggplot2)
library(patchwork)
library(scales)
library(cli)
library(lubridate)
library(reprex)
library(tidyverse)
library(geosphere)
library(reshape2)
library(moderndive)
library(skimr)
library(ggridges)
library(GGally)
library(psych)
library(raster)
library(PBSmapping)
library(sf)
library(terra)
library(knitr)
library(kableExtra)
library(grid)
library(gridExtra)
library(cowplot)
library(DT)
library(dygraphs)
library(leaflet)
library(rmapshaper)
library(plotly)
library(mapproj)
library(oce) #new CTD Data package
library(pander)
library(geodata)
library(pacman)
library(rnaturalearth)
library(rnaturalearthdata)
library(raster)
library(devtools)
library(maps)
library(dplyr)

install.packages('GADMTools')
install.packages("Rtools44")
state_prov <- rnaturalearth::ne_states(c("united states of america", "canada"))

# Survey Data
surveyData <- read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/Survey Data.csv")
# Grounds Data for Polygons
polysT = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/timGrounds.csv") #Tagging Data
#CTD Data
SST = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/CTD SST.csv") #SST
CTD = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/CTD Full.csv") #All Data
          atDepth = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/CTD 30m.csv") #At 30m Depth > This one contains all Stratified Temp + Salinity data as well
          SST$Year <- as.factor(SST$Year)
          SST$Month <- as.factor(SST$Month)
          atDepth$Year <- as.factor(atDepth$Year)
          atDepth$Month <- as.factor(atDepth$Month)
          CTD$Year <- as.factor(CTD$Year)
          CTD$Month <- as.factor(CTD$Month)
          CTD$Survey <- as.factor(CTD$Survey)
          CTD <- CTD %>%
            mutate(Julian_factor = Julian)
          CTD$Julian_factor <- as.factor(CTD$Julian_factor)

#SSB Data
SSB = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/SSB Estimates.csv")
SSB$Year <- as.factor(SSB$Year)
SSB$Survey_Number <- as.factor(SSB$Survey_Number)
SSB$Ground <- as.factor(SSB$Ground)

#LRP Data
LRP2 = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/LRP Data.csv")
LRP2 = LRP2 %>% rename(ThreeYear = "3yr Avg")

#Fat Data
FatData = read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/Total Fat Data.csv")

#Larval Data
#All Adjusted Ages and Dates are originally added in Larval QC script.
#All preservative length adjustments added in in Larval QC script.
#Changed code within compendium from Lengthmm to LengthAdjustment


# The larval data
Larval = read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Full Larval.csv"))
#original was from Main Data, Jan 2025
LarvalSum = read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Main Data/LarvalSum Jan 2025.csv"))
LarvalSum$Year <- as.factor(LarvalSum$Year)

Larval$Date <- lubridate::ymd(Larval$Date)
  Larval <- dplyr::arrange(Larval, Date)
Larval$Year <- as.factor(Larval$Year)
Larval$category <- as.factor(Larval$category)
Larval$Survey.No <- as.factor(Larval$Survey.No)
Larval$MonthDay <- format(Larval$Date, "%m-%d")

#Fix this
#Larval$AdjustedJulianSpawnDate <- as.numeric(Larval$AdjustedJulianSpawnDate) #AdjustedJulianSpawnDate is the median of the min and the max spawn date provided.

#Changed to X and Y to fit in better with compendium code. These are the tow start and finish coordinates.

names(Larval)[names(Larval) =="Lon1"] <- "X"
names(Larval)[names(Larval) =="Lat1"] <- "Y"
names(Larval)[names(Larval) =="Lon2"] <- "Xend"
names(Larval)[names(Larval) =="Lat2"] <- "Yend"

#Seal Island Larval
LarvalSI = filter(Larval, Ground == "SI")
LarvalSI = merge(LarvalSI, LarvalSum[,c("id", "TowReplicate", "TowID")], by = "id")

Larval = merge(Larval, LarvalSum[,c("id", "TowReplicate", "TowID")], by = "id")

# Map data
can<-gadm(country='CAN', level=1, path = "geodata_default_path",version="latest", resolution = 1, regions = c("New Brunswick", "Nova Scotia"))
  NBNS <- can[can$NAME_1 %in% c("New Brunswick", "Nova Scotia"), ]
  NBNS_sf <- sf::st_as_sf(NBNS)
  NBNS = NBNS_sf


```

```{r Box Import}
#Import All Boxes
boxes <- read.csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Box Coordinates/surveyBoxes.csv")

# convert to sf
# Scots Bay plankton 
SBplankton=boxes[which(boxes$Box == "SBPlanktonBox"), ]
SBplankton_sf <- SBplankton %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")

# Scots Bay CTD
SBCTD=boxes[which(boxes$Box == "SBocean"), ]
SBCTD_sf <- SBCTD %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")


# Scots Bay Eastern
SUA = read.csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Box Coordinates/polygon_SBEastern.csv")
polyEastern = as.PolySet(SUA, projection="LL")
polyEastern_sf <- polyEastern %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")

# Scots Bay Northern
SUA = read.csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Box Coordinates/polygon_SBNorthern.csv")
polyNorthern = as.PolySet(SUA, projection="LL")
polyNorthern_sf <- polyNorthern %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")

# Scots Bay Main
SUA = read.csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Box Coordinates/polygon_SB.csv")
polySB_main = as.PolySet(SUA, projection="LL")
polySB_main_sf <- polySB_main %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")


#German Bank CTD box
GBCTD=boxes[which(boxes$Box == "GBocean"), ]
GBCTD_sf <- GBCTD %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")


# German Bank      
SUA = read.csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Box Coordinates/polygon_GB.csv")
polyGB = as.PolySet(SUA, projection="LL")
polyGB_sf <- polyGB %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")

# Seal Island      
SUA = read.csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Box Coordinates/polygon_SI.csv")
polySI = as.PolySet(SUA, projection="LL")
polySI_sf <- polySI %>%
  st_as_sf(coords = c("X", "Y"), crs = st_crs(NBNS_sf)) %>%
  group_by(PID) %>%
  summarise(geometry = st_combine(geometry)) %>%
  st_cast("POLYGON")
```

## Larval Project {.tabset}

### Scots Bay {.tabset}

#### Length Data {.tabset .tabset-pills}

##### Total 

```{r, results = "asis", fig.align='center'}
Larval1 <- subset.data.frame(Larval, Ground == "SB")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=Julian, colour = Year)) +
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Julian Date")

ggplot(Larval1, aes(Year, LengthAdjustment, colour = Year)) + 
  geom_boxplot() +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)")

Table = Larval1 %>%
  group_by(Year) %>%
  summarize(MinLength = min(LengthAdjustment),
            MaxLength = max(LengthAdjustment),
            AvgLength = mean(LengthAdjustment),
            AvgSD = mean(SD),
            Abundance = n()) %>%
  mutate_if(is.numeric, format, digits=2)

kbl(Table, col.names=c("Year", "Min Length (mm)", "Max Length (mm)", "Mean Length (mm)", "+/- SD (mm)", "Abundance"), align = "c") %>%
  kable_paper("striped", full_width = F)

TotalCategories <- Larval1 %>%
  group_by(category) %>%
  dplyr::summarize(n = n()) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  mutate(Length = ifelse(category==1, "<8", 
                  ifelse(category==2, "8-12",
                  ifelse(category==3, "13-17",
                  ifelse(category==4, "18-27",
                  ifelse(category==5, ">28", NA)))))) %>%
  relocate(Length, .after = category) %>%
    mutate(Age = ifelse(category==1, "<2 weeks", 
                  ifelse(category==2, "2-5 weeks",
                  ifelse(category==3, "5-8 weeks",
                  ifelse(category==4, "8-14 weeks",
                  ifelse(category==5, ">14 weeks", NA)))))) %>%
  relocate(Age, .after = Length)

kbl(TotalCategories, col.names=c("Category", "Length (mm)", "Age", "Abundance", "%"), align = "c") %>%
  kable_paper("striped", full_width = F)
  
```


```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
# In histogram, count is the number of individuals that fall into that length category over the whole year. It is split by colour into each individual survey. Each length category is therefore split up by number of individuals per survey.
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 <- subset.data.frame(Larval, Ground == "SB")
Larval1 = Larval1 %>% filter(Year == i)

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=Julian, colour = id)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Julian Day")

print(ggplot(data = subset(Larval1, Year == i), aes(x = Julian, y = LengthAdjustment, colour = id)) +
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  ylab("Length (mm)") + 
  xlab("Julian Day") +
  scale_y_continuous(limits = c(0, max(Larval1$LengthAdjustment))) + 
  scale_x_continuous(breaks = seq(from = 150, to = 270, by = 20)) +
  ggtitle(paste(i, "Scots Bay")))
  cat("\n")
  
print(ggplot(data = Larval1, (aes(LengthAdjustment, fill = id))) + 
  geom_histogram(binwidth=0.5, colour = "white") + 
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  labs(x = "Length (mm)", y="Count"))
  cat("\n")
  
  Table = Larval1 %>% 
  group_by(Survey.No) %>%
  summarize(AvgLength = mean(LengthAdjustment),
            AvgSD = mean(SD),
            Abundance = n()) %>%
  mutate_if(is.numeric, format, digits=2)

print(kbl(Table, col.names=c("Survey #", "Mean Length (mm)", "+/- SD (mm)", "Abundance"), align = "c") %>%
  kable_paper("striped", full_width = F))
  cat("\n")
  
  TotalCategories <- Larval1 %>%
  group_by(category) %>%
  dplyr::summarize(n = n()) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  mutate(Length = ifelse(category==1, "<8", 
                  ifelse(category==2, "8-12",
                  ifelse(category==3, "13-17",
                  ifelse(category==4, "18-27",
                  ifelse(category==5, ">28", NA)))))) %>%
  relocate(Length, .after = category) %>%
    mutate(Age = ifelse(category==1, "<2 weeks", 
                  ifelse(category==2, "2-5 weeks",
                  ifelse(category==3, "5-8 weeks",
                  ifelse(category==4, "8-14 weeks",
                  ifelse(category==5, ">14 weeks", NA)))))) %>%
  relocate(Age, .after = Length)

print(kbl(TotalCategories, col.names=c("Category", "Length (mm)", "Age", "Abundance", "%"), align = "c") %>%
  kable_paper("striped", full_width = F))
  cat("\n")
}
```

#### Mapped Data {.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE}

#CP <- as(extent(-66.5, -64.5, 44.5, 45.5), "SpatialPolygons") #set boundaries for Scots Bay before plotting
#proj4string(CP) <- CRS(proj4string(NBNS))
#out <- crop(NBNS, CP, byid=TRUE)

CP <- ext(-66.5, -64.5, 44.5, 45.5)
CP <- as.polygons(CP)
crs(CP) <- crs(NBNS)
CP_sf <- sf::st_as_sf(CP)


```

##### Total

```{r echo=FALSE, fig.align='center'}
Larval2 <- subset(Larval, Ground == 'SB')

print(
  ggplot() +
    geom_sf(data = NBNS_sf, fill = "lightgray", color = "black") +
    geom_sf(data = polySB_main_sf, fill = "white", color = "black", linetype = 3) +
    geom_sf(data = SBplankton_sf, fill = "white", color = "black", linetype = 3) +
    geom_sf(data = SBCTD_sf, fill = "white", color = "black", linetype = 3) +
    geom_sf(data = polyNorthern_sf, fill = "white", color = "black", linetype = 3) +
    geom_sf(data = polyEastern_sf, fill = "white", color = "black", linetype = 3) +
    geom_point(data = Larval2,
               aes(x = X, y = Y, fill = category),
               pch = 21, alpha = 0.6) +
    coord_sf() +
    labs(x = NULL, y = NULL)
)


```

```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

  Larval1 <- Larval %>% 
    filter(Year == i, Ground == "SB")

  print(
    ggplot(data = Larval1, aes(AvgTowDepth, LengthAdjustment, colour = id)) +
      geom_jitter(size = 1.25, width = 3) +
      geom_hline(yintercept = 8,  linetype = "longdash", size = 1, colour = "red") +
      geom_hline(yintercept = 12, linetype = "longdash", size = 1, colour = "blue") +
      geom_hline(yintercept = 17, linetype = "longdash", size = 1, colour = "forestgreen") +
      geom_hline(yintercept = 27, linetype = "longdash", size = 1, colour = "grey70") +
      scale_y_reverse() +
      labs(x = "Average Tow Depth (m)", 
           y = "Larval Length (mm)", 
           colour = "id")
  )

  cat("\n")
  
  TotalCategories <- Larval1 %>%
    group_by(category) %>%
    summarize(n = n(),
              MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
    mutate(Percentage = (n/sum(n))*100) %>%
    mutate_if(is.numeric, format, digits = 1) %>%
    relocate(MeanDepth, .after = Percentage)

  print(
    kbl(TotalCategories,
        col.names = c("Category", "Abundance", "%", "Avg Tow Depth (m)"),
        align = "c") %>%
      kable_paper("striped", full_width = FALSE)
  )

  cat("\n")
}

```









#### Depth Data {.tabset .tabset-pills}
##### Total

```{r echo=FALSE, fig.align='center'}

Larval1 = Larval %>% filter(Ground == "SB")

Larval1 %>% 
  ggplot(aes(AvgTowDepth, LengthAdjustment, colour = Year)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") + 
  scale_y_reverse() +
  labs(x = "Average Tow Depth (m)", y = "Larval Length (mm)", colour = "Category")

TotalCategories <- Larval1 %>%
  group_by(category) %>%
  summarize(n = n(),
            MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  relocate(MeanDepth, .after= Percentage)

kbl(TotalCategories, col.names=c("Category", "Abundance", "%", "Avg Tow Depth (m)"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

  Larval1 <- Larval %>% 
    filter(Year == i, Ground == "SB")

  print(
    ggplot(data = Larval1, 
           aes(AvgTowDepth, LengthAdjustment, colour = id)) +
      geom_jitter(size = 1.25, width = 3) +
      geom_hline(yintercept = 8,  linetype = "longdash", size = 1, colour = "red") +
      geom_hline(yintercept = 12, linetype = "longdash", size = 1, colour = "blue") +
      geom_hline(yintercept = 17, linetype = "longdash", size = 1, colour = "forestgreen") +
      geom_hline(yintercept = 27, linetype = "longdash", size = 1, colour = "grey70") +
      scale_y_reverse() +
      labs(x = "Average Tow Depth (m)", 
           y = "Larval Length (mm)", 
           colour = "id")
  )

  cat("\n")
  
  TotalCategories <- Larval1 %>%
    group_by(category) %>%
    summarize(n = n(),
              MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
    mutate(Percentage = (n/sum(n))*100) %>%
    mutate_if(is.numeric, format, digits = 1) %>%
    relocate(MeanDepth, .after = Percentage)

  print(
    kbl(TotalCategories,
        col.names = c("Category", "Abundance", "%", "Avg Tow Depth (m)"),
        align = "c") %>%
      kable_paper("striped", full_width = FALSE)
  )

  cat("\n")
}
```

#### Spawning Modes {.tabset .tabset-pills}

##### Total

#Growth applied to compare spawning modes.

```{r, fig.align='center'}

# The following survey's did not use a flowmeter, therefore does not have water volume or larval density. This is only applicable to surveys that larvae were caught.
# Scots Bay 2017 Survey 1, 2, 6 & 7
# Scots Bay 2019 Survey 8
# Scots Bay 2020 Survey 7
# Scots Bay 2021 Survey 9 & 10
# German Bank 2021 Survey 4 & 5
# Seal Island 2019 Survey unknown, no record in raw data of this survey.
# Overall summary can be found in Volume and Density Investigation - NAs in Full Larval Spreadsheet. Saved under science team, larval project. 


Larval1 = LarvalSum %>% filter(Ground == "SB")

print(ggplot(Larval1, aes(x = Survey.No, y = Density, colour = Year)) + 
  geom_point() + 
  ylab("Density (Abundance/Volume)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$Density))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Larval Density "))

print(ggplot(Larval1, aes(x = Survey.No, y = Abundance, colour = Year)) + 
  geom_point() + 
  ylab("Abundance (Count/Tow)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$Abundance))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Larval Abundance"))

print(ggplot(Larval1, aes(x = Survey.No, y = MeanAgeInDays, colour = Year)) + 
  geom_point() + 
  ylab("Mean Age (days)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$MeanAgeInDays))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Mean Larval Age of Each Individual Tow"))

```

```{r, results='asis', fig.align='center'}
 
for(i in unique(Larval$Year)) {
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 = Larval %>% filter(Ground == "SB")
Larval1 = Larval1 %>% filter(Year == i)

Larval1$MonthDay <- format(Larval1$Date, "%m-%d")

  
print(ggplot(data = subset(Larval1, Year == i), aes(x = as.numeric(Survey.No), y = Density, colour = MonthDay)) + 
  geom_point() + 
  ylab("Density (Abundance/Volume)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$Density))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Larval Density ")))
  cat("\n")

print(ggplot(Larval1, aes(x = as.numeric(Survey.No), y = Abundance, colour = MonthDay)) + 
  geom_point() + 
  ylab("Abundance (Larvae/Tow)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$Abundance))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Larval Abundance ")))
  cat("\n")

print(ggplot(Larval1, aes(x = as.numeric(Survey.No), y = MeanAgeInDays, colour = MonthDay)) + 
  geom_point() + 
  ylab("Mean Age (days)") + 
  xlab("Survey Number") +
  xlim(0, 10) + 
  scale_y_continuous(limits = c(0, max(Larval1$MeanAgeInDays))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, " Mean Larval Age of Each Individual Tow")))
  cat("\n")
}
```

#### Individual Spawn Dates {.tabset}

##### Total

Dates individual larvae were spawned. Used an incubation period of 14 days.

```{r, results = 'asis', echo=FALSE, fig.align='center'}
# Changed AdjustedJulianSpawnDate to JulianSpawnDate

Larval1 <- Larval %>% filter(Ground == "SB")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = Year)) +
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Spawn Date(Julian)")

#Possibly summarize this table? Use individual points for other graphs?


TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID")

print(kbl(TotalCategories, align = "c") %>%
      kable_paper("striped", full_width = F))

```

##### Year {.tabset}

```{r, results = 'asis', echo=FALSE, fig.align='center'}

for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("######", i, "\n")
  cat("\n")
  
  
Larval1 <- subset.data.frame(Larval, Ground == "SB")
Larval1 = Larval1 %>% filter(Year == i)
TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID") 

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = id)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Spawn Date (Julian)")

print(ggplot(data = subset(Larval1, Year == i), aes(x = JulianSpawnDate, y = LengthAdjustment, colour = id))+
        geom_jitter(size = 1.25, width = 3) + 
        geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
        geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
        geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
        geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
        ylab("Length (mm)") + 
        xlab("Spawn Date (Julian)") +
        scale_y_continuous(limits = c(0,32)) + 
        scale_x_continuous(breaks = seq(from = 100, to = 300, by = 20)) +
        ggtitle(paste(i, "Scots Bay")))
        cat("\n")
  
print(kbl(TotalCategories, align = "c") %>%
      kable_paper("striped", full_width = F))
    
}
```


##### Tow ID {.tabset .tabset-fade .tabset-pills}

```{r, results = 'asis', echo=FALSE, fig.align='center'}
Larval1 <- subset(Larval, Ground == "SB")

for(i in unique(Larval1$TowID)) {
  
  
  cat("\n")
  cat("######", i, "\n")
  cat("\n")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = id)) +
    geom_jitter(size = 1.25, width = 3) +
    geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  +
    geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  +
    geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") +
    geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
    labs(y="Length (mm)", x="Spawn Date (Julian)")

#when putting in the y_continuous max it drops a point. So have set to 32 and that seems to have solved the problem. Figure out a solution that can be more long term.
print(ggplot(data = subset(Larval1, TowID == i), aes(x = JulianSpawnDate, y = LengthAdjustment, colour = id))+
          geom_jitter(size = 1.25, width = 3) + 
          geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
          geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
          geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
          geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
          ylab("Length (mm)") + 
          xlab("Spawn Date (Julian)") +
          scale_y_continuous(limits = c(0,32)) + 
          scale_x_continuous(limits = c(100, 300)) +
          ggtitle(paste("Tow ID", i, "Scots Bay")))
          cat("\n")

TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID") %>% filter(TowID == i)
          
print(kbl(TotalCategories, align = "c") %>%
        kable_paper("striped", full_width = F))
        cat("\n")
}
```

### German Bank {.tabset}
#### Length Data {.tabset .tabset-pills}

##### Total

```{r echo=FALSE, fig.align='center'}

Larval = Larval %>% filter(Ground == "GB")

Larval %>% ggplot(aes(y=LengthAdjustment, x=Julian, colour = Year)) + 
  geom_jitter(size = 1.25, width = 0.75) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Julian Date")

ggplot(Larval, aes(Year, LengthAdjustment, colour = Year)) + 
  geom_boxplot() +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)")

Table = Larval %>%
  group_by(Year) %>%
  summarize(MinLength = min(LengthAdjustment),
            MaxLength = max(LengthAdjustment),
            AvgLength = mean(LengthAdjustment),
            AvgSD = mean(SD),
            Abundance = n()) %>%
  mutate_if(is.numeric, format, digits=2)

kbl(Table, col.names=c("Year", "Min Length (mm)", "Max Length (mm)", "Mean Length (mm)", "+/- SD (mm)", "Abundance"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

```{r, results = "asis", fig.align='center'}

Larval1 = Larval %>% filter(Ground == "GB")

for(i in unique(Larval$Year)) {
  
# In histogram, count is the number of individuals that fall into that length category over the whole year. It is split by colour into each individual survey. Each length category is therefore split up by number of individuals per survey.
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 = Larval1 %>% filter(Year == i)

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=Julian, colour = id)) + 
  geom_point() +
  labs(y="Length (mm)", x="Julian Day")

print(ggplot(data = subset(Larval1, Year == i), aes(x = Julian, y = LengthAdjustment, colour = id)) + 
  geom_point() +
  geom_jitter(width = .5) +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  ylab("Length (mm)") + 
  xlab("Julian Day") +
  scale_y_continuous(limits = c(0, max(Larval1$LengthAdjustment))) + 
  scale_x_continuous(breaks = seq(from = min(Larval1$Julian), to = max(Larval1$Julian), by = 2)) +
  ggtitle(paste(i, "German Bank")))
  cat("\n")
 
print(ggplot(data = Larval1, (aes(LengthAdjustment, fill = id))) + 
  geom_histogram(binwidth=0.5, colour = "white") + 
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  labs(x = "Length (mm)", y="Count"))
  cat("\n")
  
  Table = Larval1 %>% 
  group_by(Survey.No) %>%
  summarize(AvgLength = mean(LengthAdjustment),
            AvgSD = mean(SD),
            Abundance = n()) %>%
  mutate_if(is.numeric, format, digits=2)

print(kbl(Table, col.names=c("Survey #", "Mean Length (mm)", "+/- SD (mm)", "Abundance"), align = "c") %>%
  kable_paper("striped", full_width = F))
  cat("\n")
}
```

#### Mapped Data {.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE}

CP_sf <- st_as_sfc(
  st_bbox(c(
    xmin = -66.5,
    xmax = -65.75,
    ymin = 43,
    ymax = 43.7
  ), crs = st_crs(NBNS_sf))
)
```

##### Total

```{r echo=FALSE, fig.align='center'}

Larval2 <- subset(Larval, Ground == "GB")

ggplot() +
  geom_sf(data = CP_sf, fill = "grey90", color = "black") +
  geom_sf(data = polyGB_sf, fill = "white", color = "black", linetype = 3) +
  geom_sf(data = GBCTD_sf, fill = "white", color = "black", linetype = 3) +
  geom_sf(data = polySI_sf, fill = "white", color = "black", linetype = 3) +
  geom_point(
    data = Larval2,
    aes(x = X, y = Y, fill = Year),
    pch = 21, alpha = 0.6
  ) +
  labs(x = NULL, y = NULL) +
  coord_sf()

```



```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

  Larval1 <- Larval %>%
    filter(Year == i, Ground == "GB")

  print(
    ggplot() +
      geom_sf(data = CP_sf, fill = "grey90", color = "black") +
      geom_sf(data = GBCTD_sf, fill = "white", color = "black", linetype = 3) +
      geom_sf(data = polyGB_sf, fill = "white", color = "black", linetype = 3) +
      geom_sf(data = polySI_sf, fill = "white", color = "black", linetype = 3) +
      geom_point(
        data = Larval1,
        aes(x = X, y = Y, fill = category),
        pch = 21, alpha = 0.6
      ) +
      labs(x = NULL, y = NULL) +
      coord_sf()
  )

  cat("\n")

  TotalCategories <- Larval1 %>%
    group_by(category) %>%
    summarize(n = n()) %>%
    mutate(Percentage = (n/sum(n)) * 100) %>%
    mutate_if(is.numeric, format, digits = 1)

  print(
    kbl(TotalCategories,
        col.names = c("Category", "Abundance", "%"),
        align = "c") %>%
      kable_paper("striped", full_width = FALSE)
  )

  cat("\n")
}

```

#### Depth Data {.tabset .tabset-pills}
##### Total

```{r echo=FALSE, fig.align='center'}

Larval1 = Larval %>% filter(Ground == "GB")

Larval1 %>% 
  ggplot(aes(AvgTowDepth, LengthAdjustment, colour = Year)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") + 
  scale_y_reverse() +
  labs(x = "Average Tow Depth (m)", y = "Larval Length (mm)", colour = "Category") 

TotalCategories <- Larval1 %>%
  group_by(category) %>%
  summarize(n = n(),
            MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  relocate(MeanDepth, .after= Percentage)

kbl(TotalCategories, col.names=c("Category", "Abundance", "%", "Avg Tow Depth (m)"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 = Larval %>% filter(Year == i)
Larval1 = Larval1 %>% filter(Ground == "GB")
 
print(ggplot(data = Larval1, aes(AvgTowDepth, LengthAdjustment, colour = Year)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") + 
  scale_y_reverse() +
  labs(x = "Average Tow Depth (m)", y = "Larval Length (mm)", colour = "Category"))
  cat("\n")
  
  TotalCategories <- Larval1 %>%
  group_by(category) %>%
  summarize(n = n(),
            MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  relocate(MeanDepth, .after= Percentage)

print(kbl(TotalCategories, col.names=c("Category", "Abundance", "%", "Avg Tow Depth (m)"), align = "c") %>%
  kable_paper("striped", full_width = F))
  cat("\n")
}
```

#### Spawning Modes {.tabset .tabset-pills}

##### Total

Growth applied to compare spawning modes.

```{r, fig.align='center'}

#Should x be Julian date and colour be survey number instead of year?
#Need to add in Larval summary table within compendium

GBLarvalSum = LarvalSum %>% filter(Ground == "GB")

#GBLarvalSum$Density[is.na(GBLarvalSum$Density)] = 0
#GBLarvalSum$Abundance[is.na(GBLarvalSum$Abundance)] = 0
#GBLarvalSum$MeanAgeInDays[is.na(GBLarvalSum$MeanAgeInDays)] = 0

print(ggplot(GBLarvalSum, aes(x = Survey.No, y = Density, colour = Year)) + 
  geom_point() + 
  ylab("Density (Abundance/Volume)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(GBLarvalSum$Density))) +
  scale_x_continuous(limits = c(1, 10), breaks = seq(1,10,1)) +
  ggtitle("Larval Density "))

print(ggplot(GBLarvalSum, aes(x = Survey.No, y = Abundance, colour = Year)) + 
  geom_point() + 
  ylab("Abundance (Larvae/Tow)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(GBLarvalSum$Abundance))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Larval Abundance "))

print(ggplot(GBLarvalSum, aes(x = Survey.No, y = MeanAgeInDays, colour = Year)) + 
  geom_point() + 
  ylab("Mean Larval Age (days)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(GBLarvalSum$MeanAgeInDays))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Mean Larval Age of Individual Tows"))

```


```{r, results='asis', fig.align='center'}
 
for(i in unique(Larval$Year)) {
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 = LarvalSum %>% filter(Ground == "GB")
Larval1 = Larval1 %>% filter(Year == i)
#Larval1$Density[is.na(Larval1$Density)] <- 0
#Larval1$Abundance[is.na(Larval1$Abundance)] <- 0
#Larval1$MeanAgeInDays[is.na(Larval1$MeanAgeInDays)] <- 0

Larval1$MonthDay <- format(Larval1$Date, "%m-%d")

  
print(ggplot(data = subset(Larval1, Year == i), aes(x = as.numeric(Survey.No), y = Density, colour = MonthDay)) + 
  geom_point() + 
  ylab("Density (Abundance/Volume)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$Density))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Larval Density ")))
  cat("\n")

print(ggplot(Larval1, aes(x = as.numeric(Survey.No), y = Abundance, colour = MonthDay)) + 
  geom_point() + 
  ylab("Abundance (Larvae/Tow)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(Larval1$Abundance))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Larval Abundance ")))
  cat("\n")

print(ggplot(Larval1, aes(x = as.numeric(Survey.No), y = MeanAgeInDays, colour = MonthDay)) + 
  geom_point() + 
  ylab("Mean Age (days)") + 
  xlab("Survey Number") +
  xlim(0, 10) + 
  scale_y_continuous(limits = c(0, max(Larval1$MeanAgeInDays))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Mean Larval Age in Days")))
  cat("\n")
}
```

#### Individual Spawn Dates {.tabset}

##### Total

Dates individual larvae were spawned. Used an incubation period of 10 days.

```{r, results = 'asis', echo=FALSE, fig.align='center'}

Larval1 <- Larval %>% filter(Ground == "GB")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = Year)) +
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  scale_y_continuous(limits = c(0,32)) + 
  scale_x_continuous(breaks = seq(from = 150, to = 300, by = 20)) +
  labs(y="Length (mm)", x="Spawn Date(Julian)")

#Possibly summarize this table? Use individual points for other graphs?
TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID")

print(kbl(TotalCategories, align = "c") %>%
      kable_paper("striped", full_width = F))

```

##### Year {.tabset}

```{r, results = 'asis', echo=FALSE, fig.align='center'}

for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("######", i, "\n")
  cat("\n")
  
  
Larval1 <- subset.data.frame(Larval, Ground == "GB")
Larval1 = Larval1 %>% filter(Year == i)
TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID") 

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = id)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Spawn Date (Julian)")

print(ggplot(data = subset(Larval1, Year == i), aes(x = JulianSpawnDate, y = LengthAdjustment, colour = id))+
        geom_jitter(size = 1.25, width = 3) + 
        geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
        geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
        geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
        geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
        ylab("Length (mm)") + 
        xlab("Spawn Date (Julian)") +
        scale_y_continuous(limits = c(0,32)) + 
        scale_x_continuous(breaks = seq(from = 150, to = 300, by = 20)) +
        ggtitle(paste(i, "German Bank")))
        cat("\n")
  
print(kbl(TotalCategories, align = "c") %>%
      kable_paper("striped", full_width = F))
    
}
```


##### Tow ID {.tabset .tabset-fade .tabset-pills}

```{r, results = 'asis', echo=FALSE, fig.align='center'}
Larval1 <- subset(Larval, Ground == "GB")

for(i in unique(Larval$TowID)) {
  
  
  cat("\n")
  cat("######", i, "\n")
  cat("\n")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = id)) +
    geom_jitter(size = 1.25, width = 3) +
    geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  +
    geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  +
    geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") +
    geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
    labs(y="Length (mm)", x="Spawn Date (Julian)")

#when putting in the y_continuous max it drops a point. So have set to 32 and that seems to have solved the problem. Figure out a solution that can be more long term.
print(ggplot(data = subset(Larval1, TowID == i), aes(x = JulianSpawnDate, y = LengthAdjustment, colour = id))+
          geom_jitter(size = 1.25, width = 3) + 
          geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
          geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
          geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
          geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
          ylab("Length (mm)") + 
          xlab("Spawn Date (Julian)") +
          scale_y_continuous(limits = c(0,32)) + 
          scale_x_continuous(limits = c(100, 300)) +
          ggtitle(paste("Tow ID", i, "German Bank")))
          cat("\n")

TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID")
          
print(kbl(TotalCategories, align = "c") %>%
        kable_paper("striped", full_width = F))
        cat("\n")
}
```
### Seal Island {.tabset}
#### Length Data {.tabset .tabset-pills}

##### Total

```{r echo=FALSE, fig.align='center'}

Larval = LarvalSI

Larval %>% ggplot(aes(y=LengthAdjustment, x=Julian, colour = Year)) + 
  geom_point() +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  scale_x_continuous(labels = scales::label_number(1), limits = c(284, 288)) +
  labs(y="Length (mm)", x="Julian Date of Collection")

ggplot(Larval, aes(Year, LengthAdjustment, colour = Year)) + 
  geom_boxplot() +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)")

Table = Larval %>%
  group_by(Year) %>%
  summarize(MinLength = min(LengthAdjustment),
            MaxLength = max(LengthAdjustment),
            AvgLength = mean(LengthAdjustment),
            AvgSD = mean(SD),
            Abundance = n()) %>%
  mutate_if(is.numeric, format, digits=2)

kbl(Table, col.names=c("Year", "Min Length (mm)", "Max Length (mm)", "Mean Length (mm)", "+/- SD (mm)", "Abundance"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
# In histogram, count is the number of individuals that fall into that length category over the whole year. It is split by colour into each individual survey. Each length category is therefore split up by number of individuals per survey.
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 = LarvalSI %>% filter(Year == i)

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=Julian, colour = id)) + 
  geom_point() +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Julian Day")

print(ggplot(data = subset(Larval1, Year == i), aes(x = Julian, y = LengthAdjustment, colour = id)) + 
  geom_point() +
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  geom_jitter(width = .5) +
  ylab("Length (mm)") + 
  xlab("Julian Day") +
  scale_y_continuous(limits = c(0, max(Larval1$LengthAdjustment))) + 
  scale_x_continuous(breaks = seq(from = min(Larval1$Julian), to = max(Larval1$Julian), by = 2)) +
  ggtitle(paste(i, "Seal Island")))
  cat("\n")
 
print(ggplot(data = Larval1, (aes(LengthAdjustment, fill = id))) + 
  geom_histogram(binwidth=0.5, colour = "white") + 
  theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
  labs(x = "Length (mm)", y="Count"))
  cat("\n")
  
## This is the same plot but a different format.
  
#print(ggplot(data=Larval1, aes(LengthAdjustment, colour = Survey.No)) + 
#  geom_freqpoly(bins=100, linewidth = 1) +
#  labs(y="Count", x="Length (mm)"))
#  cat("\n")
  
  Table = Larval1 %>% 
  group_by(Survey.No) %>%
  summarize(AvgLength = mean(LengthAdjustment),
            AvgSD = mean(SD),
            Abundance = n()) %>%
  mutate_if(is.numeric, format, digits=2)

print(kbl(Table, col.names=c("Survey #", "Mean Length (mm)", "+/- SD (mm)", "Abundance"), align = "c") %>%
  kable_paper("striped", full_width = F))
  cat("\n")
}
```



#### Mapped Data {.tabset .tabset-pills}

```{r message=FALSE, warning=FALSE}

# bounding box
CP_sf <- st_as_sfc(
  st_bbox(c(
    xmin = -66.5,
    xmax = -65.5,
    ymin = 43,
    ymax = 44
  ), crs = st_crs(NBNS_sf))
)

# crop NBNS to bounding box
out_sf <- st_intersection(NBNS_sf, CP_sf)
```

##### Total

```{r echo=FALSE, fig.align='center'}

Larval2 <- subset(Larval, Ground == "SI")

ggplot() +
  geom_sf(data = out_sf, fill = "grey90", color = "black") +
  geom_sf(data = polyGB_sf, fill = "white", color = "black", linetype = 3) +
  geom_sf(data = GBCTD_sf, fill = "white", color = "black", linetype = 3) +
  geom_sf(data = polySI_sf, fill = "white", color = "black", linetype = 3) +
  geom_point(
    data = Larval2,
    aes(x = X, y = Y, fill = Year),
    pch = 21, alpha = 0.6
  ) +
  labs(x = NULL, y = NULL) +
  coord_sf()
```



```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

  Larval1 <- Larval %>%
    filter(Year == i, Ground == "SI")   # or GB/SI depending on your region

  print(
    ggplot() +
      geom_sf(data = out_sf, fill = "grey90", color = "black") +
      geom_sf(data = GBCTD_sf, fill = "white", color = "black", linetype = 3) +
      geom_sf(data = polyGB_sf, fill = "white", color = "black", linetype = 3) +
      geom_sf(data = polySI_sf, fill = "white", color = "black", linetype = 3) +
      geom_point(
        data = Larval1,
        aes(x = X, y = Y, fill = category),
        pch = 21, alpha = 0.6
      ) +
      labs(x = NULL, y = NULL) +
      coord_sf()
  )

  cat("\n")

  TotalCategories <- Larval1 %>%
    group_by(category) %>%
    summarize(n = n()) %>%
    mutate(Percentage = (n/sum(n)) * 100) %>%
    mutate_if(is.numeric, format, digits = 1)

  print(
    kbl(TotalCategories,
        col.names = c("Category", "Abundance", "%"),
        align = "c") %>%
      kable_paper("striped", full_width = FALSE)
  )

  cat("\n")
}
```

#### Depth Data {.tabset .tabset-pills}
##### Total

```{r echo=FALSE, fig.align='center'}

LarvalSI %>% 
  ggplot(aes(AvgTowDepth, LengthAdjustment, colour = Year)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") + 
  scale_y_reverse() +
  labs(x = "Average Tow Depth (m)", y = "Larval Length (mm)", colour = "Category") 

TotalCategories <- LarvalSI %>%
  group_by(category) %>%
  summarize(n = n(),
            MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  relocate(MeanDepth, .after= Percentage)

kbl(TotalCategories, col.names=c("Category", "Abundance", "%", "Avg Tow Depth (m)"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

```{r, results = "asis", fig.align='center'}
for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

Larval1 = LarvalSI %>% filter(Year == i)
 
print(ggplot(data = Larval1, aes(AvgTowDepth, LengthAdjustment, colour = Year)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") + 
  scale_y_reverse() +
  labs(x = "Average Tow Depth (m)", y = "Larval Length (mm)", colour = "Category"))
  cat("\n")
  
  TotalCategories <- Larval1 %>%
  group_by(category) %>%
  summarize(n = n(),
            MeanDepth = mean(AvgTowDepth, na.rm = TRUE)) %>%
  mutate(Percentage = (n/sum(n))*100) %>%
  mutate_if(is.numeric, format, digits = 1) %>%
  relocate(MeanDepth, .after= Percentage)

print(kbl(TotalCategories, col.names=c("Category", "Abundance", "%", "Avg Tow Depth (m)"), align = "c") %>%
  kable_paper("striped", full_width = F))
  cat("\n")
}
```

#### Spawning Modes {.tabset .tabset-pills}

##### Total

Growth applied to compare spawning modes.

```{r, fig.align='center'}

LarvalSum = LarvalSum %>% filter(Ground == "SI")

print(ggplot(LarvalSum, aes(x = Survey.No, y = Density, colour = Year)) + 
  geom_point() + 
  ylab("Density (Abundance/Volume)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(LarvalSum$Density))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Larval Density "))

print(ggplot(LarvalSum, aes(x = Survey.No, y = Abundance, colour = Year)) + 
  geom_point() + 
  ylab("Abundance (Larvae/Tow)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(LarvalSum$Abundance))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Larval Abundance "))

print(ggplot(LarvalSum, aes(x = Survey.No, y = MeanAgeInDays, colour = Year)) + 
  geom_point() + 
  ylab("Mean Age (days)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(LarvalSum$MeanAgeInDays))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle("Mean Larval Age in Days"))

```


```{r, results='asis', fig.align='center'}
 
for(i in unique(Larval$Year)) {
  cat("\n")
  cat("#####", i, "\n")
  cat("\n")

LarvalSum = LarvalSum %>% filter(Year == i)
#LarvalSum$Density[is.na(LarvalSum$Density)] <- 0
#LarvalSum$Abundance[is.na(LarvalSum$Abundance)] <- 0
#LarvalSum$MeanAgeInDays[is.na(LarvalSum$MeanAgeInDays)] <- 0

LarvalSum$MonthDay <- format(LarvalSum$Date, "%m-%d")

  
print(ggplot(data = subset(LarvalSum, Year == i), aes(x = as.numeric(Survey.No), y = Density, colour = MonthDay)) + 
  geom_point() + 
  ylab("Density (Abundance/Volume)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(LarvalSum$Density))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Larval Density ")))
  cat("\n")

print(ggplot(LarvalSum, aes(x = as.numeric(Survey.No), y = Abundance, colour = MonthDay)) + 
  geom_point() + 
  ylab("Abundance (Larvae/Tow)") + 
  xlab("Survey Number") +
  scale_y_continuous(limits = c(0, max(LarvalSum$Abundance))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Larval Abundance ")))
  cat("\n")

print(ggplot(LarvalSum, aes(x = as.numeric(Survey.No), y = MeanAgeInDays, colour = MonthDay)) + 
  geom_point() + 
  ylab("Mean Age (days)") + 
  xlab("Survey Number") +
  xlim(0, 10) + 
  scale_y_continuous(limits = c(0, max(LarvalSum$MeanAgeInDays))) +
  scale_x_continuous(breaks = seq(0, 10, 1)) +
  ggtitle(paste(i, "Mean Larval Age of Each Individual Tow")))
  cat("\n")
}
```

#### Individual Spawn Dates {.tabset}

##### Total

Dates individual larvae were spawned. Used an incubation period of 10 days.

```{r, results = 'asis', echo=FALSE, fig.align='center'}

Larval1 <- Larval %>% filter(Ground == "SI")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = Year)) +
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Spawn Date(Julian)")

#Possibly summarize this table? Use individual points for other graphs?
TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID")

print(kbl(TotalCategories, align = "c") %>%
      kable_paper("striped", full_width = F))

```

##### Year {.tabset}

```{r, results = 'asis', echo=FALSE, fig.align='center'}

Larval1 <- subset.data.frame(Larval, Ground == "SI")

for(i in unique(Larval$Year)) {
  
  cat("\n")
  cat("######", i, "\n")
  cat("\n")
  
Larval1 = Larval1 %>% filter(Year == i)
TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID") 

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = id)) + 
  geom_jitter(size = 1.25, width = 3) + 
  geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
  geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
  geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
  geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
  labs(y="Length (mm)", x="Spawn Date (Julian)")

print(ggplot(data = subset(Larval1, Year == i), aes(x = JulianSpawnDate, y = LengthAdjustment, colour = id))+
        geom_jitter(size = 1.25, width = 3) + 
        geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
        geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
        geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
        geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
        ylab("Length (mm)") + 
        xlab("Spawn Date (Julian)") +
        scale_y_continuous(limits = c(0,30)) + 
        scale_x_continuous(breaks = seq(from = 150, to = 300, by = 20)) +
        ggtitle(paste(i, "Seal Island")))
        cat("\n")
  
print(kbl(TotalCategories, align = "c") %>%
      kable_paper("striped", full_width = F))
    
}
```


##### Tow ID {.tabset .tabset-fade .tabset-pills}

```{r, results = 'asis', echo=FALSE, fig.align='center'}
Larval1 <- subset(Larval, Ground == "SI")

for(i in unique(Larval$TowID)) {
  
  
  cat("\n")
  cat("######", i, "\n")
  cat("\n")

Larval1 %>% ggplot(aes(y=LengthAdjustment, x=JulianSpawnDate, colour = id)) +
    geom_jitter(size = 1.25, width = 3) +
    geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  +
    geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  +
    geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") +
    geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
    labs(y="Length (mm)", x="Spawn Date (Julian)")

#when putting in the y_continuous max it drops a point. So have set to 32 and that seems to have solved the problem. Figure out a solution that can be more long term.
print(ggplot(data = subset(Larval1, TowID == i), aes(x = JulianSpawnDate, y = LengthAdjustment, colour = id))+
          geom_jitter(size = 1.25, width = 3) + 
          geom_hline(yintercept = 8, linetype = "longdash", size =1, colour = "red")  + 
          geom_hline(yintercept = 12, linetype = "longdash", size =1, colour = "blue")  + 
          geom_hline(yintercept = 17, linetype = "longdash", size =1, colour = "forestgreen") + 
          geom_hline(yintercept = 27, linetype = "longdash", size =1, colour = "grey70") +
          ylab("Length (mm)") + 
          xlab("Spawn Date (Julian)") +
          scale_y_continuous(limits = c(0,32)) + 
          scale_x_continuous(limits = c(100, 300)) +
          ggtitle(paste("Tow ID", i, "Seal Island")))
          cat("\n")

TotalCategories <- Larval1 %>% select("id", "Date", "Survey.No", "LengthAdjustment", "JulianSpawnDate", "TowReplicate", "TowID")
          
print(kbl(TotalCategories, align = "c") %>%
        kable_paper("striped", full_width = F))
        cat("\n")
}
```

:::
:::
