---
title: ""
output:
  rmdformats::html_clean:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
rm(list = ls())
#Change these options
surv = "SB"
surv2 = "Scots Bay"
surv.date = "2022-01-01 20:00"
surv.no = "6"
Allocation = "150"
SIAllocation = "75"
vessels = 8
EVessel = "Morning Star"
NVessel = NA
PlanktonVessel = "Lady Janice II"
Tagging = c("Morning Star", "Lady Janice II", "Sealife II", "Tasha Marie")

knitr::opts_knit$set(root.dir = paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/"))
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, fig.align='center')
```

```{r Data Import, include=FALSE}
#Import all packages and data
library(cli)
library(lubridate)
library(reprex)
library(tidyverse)
library(geosphere)
library(reshape2)
library(moderndive)
library(skimr)
library(ggridges)
library(weathercan)
library(GGally)
library(psych)
library(raster)
library(PBSmapping)
library(rgeos)
library(knitr)
library(kableExtra)
library(grid)
library(gridExtra)
library(cowplot)

#Parse date time
surv.date = as.POSIXlt(surv.date, format="%Y-%m-%d %H:%M")
StartTime = substr(surv.date, 12,16)
StartDate = substr(surv.date, 1,10)
year = substr(surv.date, 1,4)

#Load plan
setwd(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/"))
Plan = list.files(pattern = "*plan.csv") %>% 
  map_df(~read_csv(.))

Table = list.files(pattern = "*Table.csv") %>% 
  map_df(~read_csv(.))

#Land Data
setwd(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/"))
can<-getData('GADM', country="CAN", level=1)
us = getData('GADM', country = "USA", level = 1)
can1 = rbind(can,us)
NBNS <- can1[can1@data$NAME_1%in%c("New Brunswick","Nova Scotia","Prince Edward Island","Newfoundland and Labrador","Québec", "Maine"),]

# Proper coordinates for German Bank
GBMap <- as(extent(-66.5, -65.5, 43, 44), "SpatialPolygons")
proj4string(GBMap) <- CRS(proj4string(NBNS))
GBout <- gIntersection(NBNS, GBMap, byid=TRUE)

# Proper coordinates for Scots Bay
SBMap <- as(extent(-65.5, -64.5, 45, 45.5), "SpatialPolygons")
proj4string(SBMap) <- CRS(proj4string(NBNS))
SBout <- gIntersection(NBNS, SBMap, byid=TRUE)

#Make CTD Cast Box (GB or SB)
a = c("4334.320", "4333.600", "4333.600", "4334.320")
b = c("6622.080", "6622.080", "6621.000", "6621.000")
c = c("4503.432", "4503.000", "4503.000", "4503.432")
d = c("6513.048", "6513.048", "6512.000", "6512.000")

if(surv == "SB") {
  CTDBox = data.frame(c,d)
  names(CTDBox) = c('Lat', 'Lon')
}

if(surv == "GB") {
  CTDBox = data.frame(a,b)
  names(CTDBox) = c('Lat', 'Lon')
}

#Make Tow Box (SB only)
a = c("4501.800", "4504.200", "4506.780", "4504.500")
b = c("6515.300", "6506.600", "6506.600", "6515.300")
TowBox = data.frame(a,b)
names(TowBox) = c('Lat', 'Lon')
```

```{r Box Import}
#Import All Boxes
setwd(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Box Coordinates/"))
boxes = read.csv("surveyBoxes.csv")

# Scots Bay plankton and CTD box
SBplankton=boxes[which(boxes$Box == "SBPlanktonBox"), ]
SBCTD=boxes[which(boxes$Box == "SBocean"), ]

# Scots Bay
SUA = read.csv("polygon_SBEastern.csv")
polyEastern = as.PolySet(SUA, projection="LL")

SUA = read.csv("polygon_SBNorthern.csv")
polyNorthern = as.PolySet(SUA, projection="LL")

SUA = read.csv("polygon_SB.csv")
polySB_main = as.PolySet(SUA, projection="LL")

#German Bank CTD box
GBCTD=boxes[which(boxes$Box == "GBocean"), ]

# German Bank      
SUA = read.csv("polygon_GB.csv")
polyGB = as.PolySet(SUA, projection="LL")

# Seal Island      
SUA = read.csv("polygon_SI.csv")
polySI = as.PolySet(SUA, projection="LL")
```

### `r surv2` Survey \#`r surv.no` - `r StartDate` {.tabset}

This survey will include `r vessels` participating vessels. 

```{r echo=FALSE}
a=if(surv == "SB" & !is.na(EVessel) & !is.na(NVessel)){
  paste(EVessel, "and", NVessel, "will run 4 lines in the East and North boxes, and all other vessels will be running 2 lines in the Main Survey Box")
}

b=if(surv == "SB" & is.na(EVessel) & !is.na(NVessel)){
  paste(NVessel, "will run 4 lines in the North box, and all other vessels will be running 2 lines in the Main Survey Box")
}

c=if(surv == "SB" & is.na(EVessel) & is.na(NVessel)){
  "All vessels will be running 2 lines in the Main Survey Box"
}

d=if(surv=="GB"){
  "All vessels are to complete two lnes each in the German Survey Box and one line in the Seal Island Box"
}

e=if(surv == "SB" & !is.na(EVessel) & is.na(NVessel)){
  paste(EVessel, "will run 4 lines in the East box, and all other vessels will be running 2 lines in the Main Survey Box")
}
```

Vessels will complete the following lines: `r a` `r b` `r c` `r d` `r e`.

The survey will have a start time of `r StartTime`. 

The `r PlanktonVessel` will conduct plankton tows and oceanographic sampling. 

Tagging with be conducted from the `r Tagging`.

```{r}
c=if(surv=="SB"){
  "Vessels are reminded to complete their assigned transects as listed, straight, and without deviating. Afterwards, school surveying can be conducted while waiting to begin fishing but not before the assigned transects have been completed. Please run at least 3 parallel lines over the school and ensure the fishing sonars are turned off. "
}
```

`r c`

 **When running your transect, if you are recording a school of fish but are near the end of your line, please continue recording in a straight line even if it extends beyond the boundaries of the survey box.**

### Transects figure

```{r, out.width="525px", out.height="275px"}
Plan2 = Plan %>%
  dplyr::select(X = "Start Lon", Y = "Start Lat", Xend = "End Lon", Yend = "End Lat", Vessel)

if(surv=="GB"){a = ggplot(Plan2, aes(x=X, y=Y)) + 
  geom_polygon(data=GBout,aes(x=long, y=lat, group=group), fill = "gray") + 
  geom_polygon(data=GBCTD,aes(x=X, y=Y, group=PID),fill='white',col='black') +
  geom_segment(data=Plan2, aes(x = X, y = Y, xend = Xend, yend = Yend, colour = Vessel), size=1) + 
  coord_map() + 
  labs(x=NULL, y=NULL, caption = "Figure 1. Survey lines to be completed by participating vessels.")}

if(surv=="SB"){a = ggplot(Plan2, aes(x=X, y=Y)) + 
    geom_polygon(data=SBout,aes(x=long, y=lat, group=group), fill = "gray") + 
    geom_segment(data=Plan2, aes(x = X, y = Y, xend = Xend, yend = Yend, colour = Vessel), size=1) + 
    coord_map() + 
    labs(x=NULL, y=NULL, caption = "Figure 1. Survey lines to be completed by participating vessels.")}

print(a)
```

```{r}
a=if(surv=="SB"){
  paste0(PlanktonVessel, " will complete both plankton towing (bottom left outer box) and CTD casts (inner box)")
}
b=if(surv=="GB"){
  paste0(PlanktonVessel, "will complete both plankton towing and CTD casts (northern small box)")
}
```

The `r a` `r b`.

\newpage

```{r, results ="asis"}
if(surv=="SB"){
  cat("\n")
  cat("### CTD and Tow Boxes", "\n")
  cat("\n")
  kbl(list(CTDBox, TowBox)) %>%
  kable_paper("striped", full_width = F)
}

if(surv=="GB"){
  cat("\n")
  cat("### CTD Box", "\n")
  cat("\n")
  kbl(CTDBox) %>%
  kable_paper("striped", full_width = F)
}
```

### Full Lines Table

```{r}
kbl(Table) %>%
  kable_paper("striped", full_width = F) 
```

\newpage

### Instructions

1. Plan to arrive at the starting point 30 minutes before the start time of `r StartTime`.

2. Start the EK80 software and load the ‘Herring Survey 2023’ settings. When you are ready to
begin, Record Raw should be turned ‘ON’ and the ‘REC’ dot in the upper left should turn
from black to red. Finally, check that the lat and long in the top center of the screen is
changing.

3. Commence surveying first line at `r StartTime` and maintain a speed at 8 knots.

4. Run your lines straight and double check that the recorder is turned on and red.

5. Maintain deck sheets as a backup to recorders every 15 minutes.

6. Note the time when finished your last line.

```{r, include="FALSE"}
b=surv.date+days(1)
c=substr(b,1,10)
d=paste0(Allocation, "mt/vessel.")
e=paste0(Allocation, "mt/vessel for German Bank and ", SIAllocation, "mt/vessel for Seal Island.")
f=if(surv=="SB"){
  print(d)
}
g=if(surv=="GB"){
  print(e)
}
```

7. Fishing to start on `r c`, and allocation is `r f` `r g`

```{r, results="asis"}
if(surv=="SB"){
  cat("\n")
  cat("### Tidal Charts", "\n")
  cat("\n")
  knitr::include_graphics(path=paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/Hourly.jpg"), rel_path = FALSE)
}
```

```{r}
if(surv=="SB"){
    knitr::include_graphics(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/Daily.jpg"), rel_path = FALSE)
}
```