---
title: ""
output:
  rmdformats::html_clean:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
rm(list = ls()) #removes everything in the current environment

#Change these options
surv = "SB"
surv2 = "Scots Bay"
surv.date = "2025-05-06 20:00:00" #survey date and time, as formatted
surv.no = "1"
Allocation = "0" #set to "0" for a non-fishing survey
SIAllocation = "0" #Seal Island allocation for GB-only
Tagging = NA #list vessel names in a single quote string (e.g. "Lady Melissa and Sealife II")

#Set vessels below
vessels = 3
EVessel = "Brunswick Provider" #Set NA for GB or excluding box
NVessel = "Canada 100" #Set NA for GB or excluding box
PlanktonVessel = NA

#Main box only (e.g. if vessels = 9 with both SB boxes, should have 1 Evessel, 1 Nvessel, and 7 Vessels below)
V1 = "Brunswick Provider"
V2 = "Lady Melissa"
V3 = "Canada 100"
V4 = NA
V5 = NA
V6 = NA
V7 = NA
V8 = NA
V9 = NA

knitr::opts_knit$set(root.dir = paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/")) #sets the root directory for the entire document, when it isnt changed elsewhere by setwd()
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, fig.align='center') #sets the coding chunk options of the whole document to not appear in the actual document (echo)
```

```{r Data Import, include=FALSE}
#Import all packages and data
library(ggplot2)
library(patchwork)
library(scales)
library(cli)
library(lubridate)
library(reprex)
library(tidyverse)
library(geosphere)
library(reshape2)
library(moderndive)
library(skimr)
library(ggridges)
#library(weathercan)
library(GGally)
library(psych)
library(raster)
library(PBSmapping)
#library(rgeos)
library(sf)
library(terra)
library(knitr)
library(kableExtra)
library(grid)
library(gridExtra)
library(cowplot)
library(DT)
library(dygraphs)
library(leaflet)
library(rmapshaper)
library(plotly)
library(mapproj)
library(oce) #new CTD Data package
library(pander)
library(geodata)
library(pacman)
library(rnaturalearth)
library(rnaturalearthdata)
library(raster)
library(devtools)
library(maps)
library(dplyr)



#Parse date time

surv.date = as.POSIXlt(surv.date, format="%Y-%m-%d %H:%M:%S")
StartTime = substr(surv.date, 12,19) #turns the 12th-19th section of surv.date into the start time (the 20:00:00 time of surv.date)
StartDate = substr(surv.date, 1,10) #turns the 1st-10th section of surv.date into the start date (the 2023-01-01 date of surv.date)
year = substr(surv.date, 1,4)


#Create Plan by combining main box with any extra boxes

Plan = read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/survey plan.csv"))
#above line is only used if a manual plan override is needed, the ignore the below code (can '#' it to temporarily disable it)

# vessels2 = ifelse(is.na(EVessel) & is.na(NVessel), vessels, #if no east + north vessels (SB), total number of main box vessels is equal to 'vessels' without changes
#            ifelse(!is.na(EVessel) & is.na(NVessel), vessels-1, #if there is an east vessel (but not north), total # of main box vessels is equal to 'vessels' minus 1
#            ifelse(is.na(EVessel) & !is.na(NVessel), vessels-1, #if there is a north vessel (but not east), total # of main box vessels is equal to 'vessels' minus 1
#            ifelse(!is.na(EVessel) & !is.na(NVessel), vessels-2, #if there is both an east + north vessel, total number of main box vessels is equal to 'vessels' minus 2
#            NA))))
# 
# Main = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/Survey Lines/", surv, "/V", vessels2, ".csv"))
# #the above line loads the default V# spreadsheets with the proper box spacing, based on number of attending vessels.
# 
# if(!is.na(NVessel)){North = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/Survey Lines/", surv, "/North_Box.csv"))}
# #if there is a NVessel this will load the North_Box.csv box outline
# if(!is.na(EVessel)){East = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/Survey Lines/", surv, "/East_Box.csv"))}
# #if there is a EVessel this will load the East_Box.csv box outline
# 
# if(!is.na(NVessel) & is.na(EVessel)){Plan = full_join(Main, North)} #if there is a north vessel (but not east), the plan combines (full join) the main box + north box
# if(is.na(NVessel) & !is.na(EVessel)){Plan = full_join(Main, East)} #if there is an east vessel (but not north), the plan combines (full join) the main box + east box
# if(!is.na(NVessel) & !is.na(EVessel)){
#   Plan = full_join(Main, North)
#   Plan = full_join(Plan, East)} #if there is both an east and north vessel, the plan combines main + north first, then this combined frame with + east box.
# if(is.na(NVessel) & is.na(EVessel)){Plan = Main} #if there is only main box vessels, the plan is equal to the main box plan with no changes.
# 
# #Add vessel names to Plan
# Plan = Plan %>% #renames the base "V#" Vessels in the plan to the actual vessel names manually listed in the first code chunk.
#   mutate(Vessel = replace(Vessel, Vessel == "V1", V1)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V2", V2)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V3", V3)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V4", V4)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V5", V5)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V6", V6)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V7", V7)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V8", V8)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "V9", V9)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "NVessel", NVessel)) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "EVessel", EVessel))
# 
# #Short-hand names and save for Update Data script usage
# Plan2 = Plan %>% #convert the vessel names (on a separate Plan2) to their shorthand forms for other tools to use
#   mutate(Vessel = replace(Vessel, Vessel == "Leroy and Barry", "LB")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Morning Star", "MS")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Canada 100", "C1")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Fundy Monarch", "FM")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Brunswick Provider", "BP")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Lady Melissa", "LM")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Sealife II" | Vessel == "Sealife", "SL")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Lady Janice" | Vessel == "Lady Janice II", "LJ")) %>%
#   mutate(Vessel = replace(Vessel, Vessel == "Tasha Marie", "TM"))
# write_csv(x=Plan2, file=paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/survey plan.csv"))
#Comment out to here for manual plans.

#Land Data
#can<-getData('GADM', country="CAN", level=1) #getData is discontinued
can<-gadm(country='CAN', level=1, path = "geodata_default_path",version="latest", resolution = 1, regions = c("New Brunswick", "Nova Scotia", "Prince Edward Island", "Newfoundland and Labrador", "Québec"))
#us = getData('GADM', country = "USA", level = 1) # getData is discontinued
us<-gadm(country='USA', level=1, path = "geodata_default_path",version="latest", resolution = 1, regions = c("Maine"))
can1 = rbind(can,us)
NBNS = can1


#NBNS <- can1[can1@data$NAME_1%in%c("New Brunswick","Nova Scotia","Prince Edward Island","Newfoundland and Labrador","Québec", "Maine"),]
NBNS <- as(NBNS, "Spatial") #This causes it to run very slowly - takes a few minutes to process.

# Proper coordinates for German Bank
GBMap <- as(extent(-66.5, -65.5, 43, 44), "SpatialPolygons")
proj4string(GBMap) <- CRS(proj4string(NBNS))
#GBout <- gIntersection(NBNS, GBMap, byid=TRUE)
GBout <-crop(NBNS, GBMap, byid=TRUE)

# Proper coordinates for Scots Bay
SBMap <- as(extent(-65.5, -64.5, 45, 45.5), "SpatialPolygons")
proj4string(SBMap) <- CRS(proj4string(NBNS))
#SBout <- gIntersection(NBNS, SBMap, byid=TRUE)
SBout <- crop(NBNS, SBMap, byid=TRUE)

#Make CTD Cast Box (GB or SB)
a = c("4334.320", "4333.600", "4333.600", "4334.320")
b = c("6622.080", "6622.080", "6621.000", "6621.000")
c = c("4503.432", "4503.000", "4503.000", "4503.432")
d = c("6513.048", "6513.048", "6512.000", "6512.000")

#If survey is Scots Bay, load the C + D coordinates above for the CTD box
if(surv == "SB") {
  CTDBox = data.frame(c,d)
  names(CTDBox) = c('Lat', 'Lon')
}

#If survey is German Bank, load the A + B coordinates above for the CTD Box
if(surv == "GB") {
  CTDBox = data.frame(a,b)
  names(CTDBox) = c('Lat', 'Lon')
}

#Make Tow Box (SB only)
a = c("4501.800", "4504.200", "4506.780", "4504.500")
b = c("6515.300", "6506.600", "6506.600", "6515.300")
TowBox = data.frame(a,b) #combine A + B into a dataframe for the Tow Box
names(TowBox) = c('Lat', 'Lon')
```

```{r Box Import}
#Import All Boxes
setwd(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Box Coordinates/"))
boxes = read.csv("surveyBoxes.csv")

# Scots Bay plankton and CTD box
SBplankton=boxes[which(boxes$Box == "SBPlanktonBox"), ]
SBCTD=boxes[which(boxes$Box == "SBocean"), ]

# Scots Bay
SUA = read.csv("polygon_SBEastern.csv")
polyEastern = as.PolySet(SUA, projection="LL")

SUA = read.csv("polygon_SBNorthern.csv")
polyNorthern = as.PolySet(SUA, projection="LL")

SUA = read.csv("polygon_SB.csv")
polySB_main = as.PolySet(SUA, projection="LL")

#German Bank CTD box
GBCTD=boxes[which(boxes$Box == "GBocean"), ]

# German Bank      
SUA = read.csv("polygon_GB.csv")
polyGB = as.PolySet(SUA, projection="LL")

# Seal Island      
SUA = read.csv("polygon_SI.csv")
polySI = as.PolySet(SUA, projection="LL")
```

```{r}
#if the Survey is German Bank, it will be stated as non-fishing (in **bold**)
if(surv == "GB"){
  a=paste0("**", "non-fishing", "**")
}

#if the Survey is Scots Bay, it will be a 'fishing' survey.
if(surv == "SB") {
  a="fishing"
}
```


### `r surv2` Survey \#`r surv.no` - `r StartDate` {.tabset}

This `r a` survey will include `r vessels` participating vessels. 

```{r echo=FALSE}
#various combinations of which boxes are being used (north, east, none, etc), to determine a statement of which lines vessels are running
a=if(surv == "SB" & !is.na(EVessel) & !is.na(NVessel)){
  #paste(EVessel, "and", NVessel, "will run 4 lines in the East and North boxes, and all other vessels will be running 2 lines in the Main Survey Box")
  paste(EVessel, "will run 2 lines in the Main Box and 2 lines in the East Box and", NVessel, "will run 1 line in the Main Box and 4 lines in the North box.")
  }

b=if(surv == "SB" & is.na(EVessel) & !is.na(NVessel)){
  paste(NVessel, "will run 4 lines in the North box, and all other vessels will be running 2 lines in the Main Survey Box")
}

c=if(surv == "SB" & is.na(EVessel) & is.na(NVessel)){
  "All vessels will be running 2 lines in the Main Survey Box"
}

# change between one and two lines in Seal box as needed.
d=if(surv=="GB"){
  "All vessels are to complete two lines each in the German Survey Box and two line in the Seal Island Box"
}

e=if(surv == "SB" & !is.na(EVessel) & is.na(NVessel)){
  paste(EVessel, "will run 4 lines in the East box, and all other vessels will be running 2 lines in the Main Survey Box")
}

#Statement which only appears if Tagging is not NA
f=if(!is.na(Tagging)){
  paste0("Tagging will be conducted from the ", Tagging, ".")
}

```

Vessels will complete the following lines: `r a` `r b` `r c` `r d` `r e`.

The `r PlanktonVessel` will conduct plankton tows and oceanographic sampling.

The survey will have a start time of `r StartTime`. 

`r f`

```{r}
c="Vessels are reminded to complete their assigned transects as listed, straight, and without deviating."

#Afterwards, school surveying can be conducted while waiting to begin fishing but not before the assigned transects have been completed. Please run at least 3 parallel lines over the school and ensure the fishing sonars are turned off. 
```

`r c`

 **When running your transect, if you are recording a school of fish but are near the end of your line, please continue recording in a straight line even if it extends beyond the boundaries of the survey box.**

```{r, fig.width=7, fig.height=4}

#Not sure why the dplyr::select isn't working (2025) when it worked all 2024 season.

Plan2 = Plan %>%
  # dplyr::select(X = "Start Lon", Y = "Start Lat", Xend = "End Lon", Yend = "End Lat", Vessel)
  dplyr::select(X, Y, Xend, Yend, Vessel)

if(surv=="GB"){
  a = 
  ggplot(Plan2, aes(x=X, y=Y)) + 
  geom_segment(aes(x = X, y = Y, xend = Xend, yend = Yend, colour = Vessel), size=1) +
  geom_polygon(data=GBout,aes(x=long, y=lat, group=group), fill = "gray") + 
  geom_polygon(data=GBCTD,aes(x=X, y=Y, group=PID),fill='white',col='black') +
  coord_map() + 
  labs(x=NULL, y=NULL, caption = "Figure 1. Survey lines to be completed by participating vessels.")}

if(surv=="SB"){a = ggplot(Plan2, aes(x=X, y=Y)) + 
    geom_polygon(data=SBout,aes(x=long, y=lat, group=group), fill = "gray") + 
    geom_polygon(data=SBplankton,aes(x=X, y=Y, group=PID),fill='white',col='black') +
    geom_polygon(data=SBCTD,aes(x=X, y=Y, group=PID),fill='white',col='black') +
    geom_segment(data=Plan2, aes(x = X, y = Y, xend = Xend, yend = Yend, colour = Vessel), size=0.5) +
    coord_map() + 
    labs(x=NULL, y=NULL, caption = "Figure 1. Survey lines to be completed by participating vessels.")}

print(a)
```

```{r}
a=if(surv=="SB"){
  paste0(PlanktonVessel, " will complete both plankton towing (bottom left outer box) and CTD casts (inner box)")
}
b=if(surv=="GB"){
  paste0(PlanktonVessel, " will complete both plankton towing and CTD casts (northern small box)")
}
```

The `r a` `r b`.

```{r}
if(surv=="SB"){
  kables(list(
  kable(CTDBox, caption = "CTD Box") %>%
  kable_styling(full_width = FALSE, position = "float_left"),
  kable(TowBox, caption = "Tow Box") %>%
  kable_styling(full_width = FALSE, position = "right")))
}

if(surv=="GB"){
  kbl(CTDBox, caption = "CTD Box") %>%
  kable_styling(full_width = FALSE)
}
```

##### Full Lines Table

```{r}

Main = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/2025/", surv, surv.no, "/", "Table.csv"))
# use the above if manual plan. Remember to change year if needed.

#Add vessel names to Plan
Plan = Main %>%
  mutate(Vessel = replace(Vessel, Vessel == "V1", V1)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V2", V2)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "v3", V3)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "v4", V4)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V5", V5)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V6", V6)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V7", V7)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V8", V8)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V9", V9)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V10", NVessel)) %>%
  mutate(Vessel = replace(Vessel, Vessel == "V11", EVessel))

#if manual plan, read Table file and comment out below

# if(surv=="SB"){vessels2 = ifelse(is.na(EVessel) & is.na(NVessel), vessels,
#             ifelse(!is.na(EVessel) & is.na(NVessel), vessels-1,
#             ifelse(is.na(EVessel) & !is.na(NVessel), vessels-1,
#             ifelse(!is.na(EVessel) & !is.na(NVessel), vessels-2,
#             NA))))}
#  if(surv=="GB"){vessels2=vessels}
# 
#  Main = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/Survey Lines/", surv, "/C", vessels2, ".csv"))
# 
# 
#  if(surv=="SB"){
#  if(!is.na(NVessel)){North = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/Survey Lines/", surv, "/North_Box_Captains.csv"))}
#  if(!is.na(EVessel)){East = read_csv(paste0("C:/Users/", Sys.info()[7], "/Documents/GitHub/HerringScience.github.io/Surveys/Survey Lines/", surv, "/East_Box_Captains.csv"))}
#  if(!is.na(NVessel) & is.na(EVessel)){Plan = full_join(Main, North)}
#  if(is.na(NVessel) & !is.na(EVessel)){Plan = full_join(Main, East)}
#  if(!is.na(NVessel) & !is.na(EVessel)){
#    Plan = full_join(Main, North)
#    Plan = full_join(Plan, East)}
#  if(is.na(NVessel) & is.na(EVessel)){Plan = Main}}
#  if(surv=="GB"){Plan=Main}

#Comment out to here

#Add vessel names to Plan.
 Plan = Plan %>%
   mutate(Vessel = replace(Vessel, Vessel == "V1", V1)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V2", V2)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V3", V3)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V4", V4)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V5", V5)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V6", V6)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V7", V7)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V8", V8)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "V9", V9)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "NVessel", NVessel)) %>%
   mutate(Vessel = replace(Vessel, Vessel == "EVessel", EVessel))

Plan %>%
  arrange(Vessel) %>%
  kbl() %>%
  kable_styling(., full_width = FALSE)
   
```

### Instructions

1. Plan to arrive at the starting point 30 minutes before the start time of `r StartTime`.

2. Start the EK80 software and load the ‘Herring Survey 2024’ settings. When you are ready to
begin, Record Raw should be turned ‘ON’ and the ‘REC’ dot in the upper left should turn
from black to red. Finally, check that the lat and long in the top center of the screen is
changing.

3. Commence surveying first line at `r StartTime` and maintain a speed at 8 knots.

4. Run your lines straight and double check that the recorder is turned on and red.

5. Maintain deck sheets as a backup to recorders every 15 minutes.

6. Note the time when finished your last line.

```{r, include="FALSE"}

b=surv.date+days(1)
c=substr(b,1,10)
d=paste0(Allocation, "mt/vessel.")
e=paste0(Allocation, "mt/vessel for German Bank and ", SIAllocation, "mt/vessel for Seal Island.")
i= "7. This is a non-fishing survey."
h=if(Allocation == 0){
  print(i)
}
f=if(surv=="SB" & Allocation != 0){
  paste0("7. Fishing to start on ", c, ", and allocation is ", d)
}
g=if(surv=="GB" & Allocation != 0){
  paste0("7. Fishing to start on ", c, ", and allocation is ", e)
}
```

`r g` `r f` `r h`

```{r, results="asis"}
if(surv=="SB"){
  cat("\n")
  cat("### Tidal Charts", "\n")
  cat("\n")
  knitr::include_graphics(path=paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/Hourly.jpg"), rel_path = FALSE)
}
```

```{r}
if(surv=="SB"){
    knitr::include_graphics(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/Daily.jpg"), rel_path = FALSE)
}
```

```{r, include = "FALSE"}
#save all changes and information to a .csv for Update Data and results
CurrentData = tibble(FlowmeterType = "General Oceanics", TowType = "Surface Tow", Gear = "1/500", PlanktonVessel = PlanktonVessel, EVessel = EVessel, NVessel = NVessel, Survey.No = surv.no, Ground = surv, Vessel.No = vessels, Net = "1")
Month = substr(StartDate, 6,7)
Day = substr(StartDate, 9,10)
Year = substr(StartDate, 1,4)
CurrentData$Date = as.character(paste0(Day,"/",Month,"/",Year))
CurrentData$StartTime = as.character(StartTime)
CurrentData = CurrentData %>%
  mutate(ExtraBox = ifelse(!is.na(EVessel) & is.na(NVessel), "East",
                    ifelse(is.na(EVessel) & !is.na(NVessel), "North",
                    ifelse(!is.na(EVessel) & !is.na(NVessel), "Both",
                    ifelse(is.na(EVessel) & is.na(NVessel), "None",
                           NA))))) %>%
  mutate(Fishing = ifelse(Allocation > 0 | !is.na(Allocation), "Y", "N")) %>%
  mutate(PlanktonVessel = ifelse(PlanktonVessel == "Lady Janice", "Lady Janice II", PlanktonVessel))
CurrentData %>% write_csv((paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Surveys/", year, "/", surv, surv.no, "/Plan Data.csv")))
```