---
title: "tagReturnsTracey Markdown"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
year= substr(Sys.Date(),1,4)
knitr::opts_knit$set(root.dir = paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/"))
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, fig.align='center')

library(cli)
library(lubridate)
library(reprex)
library(tidyverse)
library(geosphere)
library(reshape2)
library(moderndive)
library(skimr)
library(ggridges)
library(GGally)
library(psych)
library(raster)
library(PBSmapping)
library(knitr)
library(kableExtra)
library(grid)
library(gridExtra)
library(cowplot)
library(dplyr)
library(geonames)
library(mgcv)
library(scales)

location_lookup <- c(
  "German Bank" = "GB",
  "German Bank (Area 7)" = "GB",
  "Scots Bay" = "SB",
  "Scots Bay (Area 8)" = "SB",
  "NB Coastal" = "NBC",
  "Grand Manan" = "GM",
  "Grand Manan Banks" = "GMB",
  "Long Island" = "LI",
  "Seal Island" = "SI",
  "Yankee Bank" = "YB",
  "Trinity" = "T",
  "Browns Bank" = "BB",
  "SW Grounds" = "SWG",
  "Gannet Dry Ledge" = "GDL",
  "Lurcher" = "L"
)

create_tag_returns <- function(data, tagging_ground) {

  origin_code <- unname(location_lookup[tagging_ground])

  data %>%
    filter(FishingGround == tagging_ground) %>%
    mutate(
      DestinationCode = location_lookup[catchAREA],
      TagLocation = ifelse(
        is.na(DestinationCode),
        "Other",
        paste(origin_code, "to", DestinationCode)
      )
    ) %>%
    filter(TagLocation != "Other")
}

create_summary_table <- function(data) {

  data %>%
    count(
      #Tim
      TagLocation,
      category,
      name = "Abundance"
    ) %>%
    arrange(TagLocation, category)
}

ground_report <- function(data, tagging_ground, remove_cat1 = TRUE) {

  tag_data <- create_tag_returns(
    data,
    tagging_ground
  )

  if (remove_cat1) {
    tag_data <- tag_data %>%
      filter(category != 1)
  }

  summary_table <- tag_data %>%
    count(
      TagLocation,
      category,
      name = "Abundance"
    ) %>%
    arrange(
      TagLocation,
      category
    )

  plot <- ggplot(
    tag_data,
    aes(
      x = TagLocation,
      fill = factor(category)
    )
  ) +
    geom_bar(colour = "white") +
    theme(
      panel.background = element_rect(
        fill = "white",
        colour = "grey50"
      )
    ) +
    labs(
      x = "Tag to Catch Location",
      y = "Number of Events",
      fill = "Category"
    ) +
    ggtitle(
      paste0(
        tagging_ground,
        " Tag Returns"
      )
    ) +
    scale_y_continuous(
      breaks = pretty_breaks()
    )

  list(
    data = tag_data,
    summary = summary_table,
    plot = plot
  )
}

plot_tag_returns <- function(data, title) {

  ggplot(
    data,
    aes(
      x = TagLocation,
      fill = factor(category)
    )
  ) +
    geom_bar(colour = "white") +
    theme(
      panel.background = element_rect(
        fill = "white",
        colour = "grey50"
      )
    ) +
    labs(
      x = "Tag to Catch Location",
      y = "Number of Events",
      fill = "Category"
    ) +
    ggtitle(title) +
    scale_y_continuous(
      breaks = pretty_breaks()
    )
}

remove_category1 <- function(data) {

  data %>%
    filter(category != 1)
}




```

``` {css, echo = FALSE}
.scoll-100 {
max-height: 100px;
overflow-y: auto;
background-colour: inherit;
}

```

```{r Data Import, include=FALSE}

completeReturns <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tagging/Tag Returns/complete.returns.csv"))
TaggingEvents <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/TaggingEvents.csv"))

names(TaggingEvents)[names(TaggingEvents) == 'Tag_Num'] <- 'TAG_NUMBER'

rawReturn <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tagging/Tag Returns/rawReturn.csv"))
#relINFO <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tag Returns/relINFO.csv"))
polysNAFO <- read_csv(paste0("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/NAFO_subunits.csv"))
polysT <- read_csv(paste0("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/timGrounds.csv"))

                           
#Combining complete Returns and Tagging events by tag number
TagReturns <- merge(TaggingEvents, completeReturns, by = "TAG_NUMBER")

# Assigning of Grounds

area1=polysT[which(polysT$Box == "NB Coastal"), ]
area2=polysT[which(polysT$Box == "Grand Manan"), ]
area3=polysT[which(polysT$Box == "Grand Manan Banks"), ]
area4=polysT[which(polysT$Box == "Long Island"), ]
area5=polysT[which(polysT$Box == "German Bank"), ]
area6=polysT[which(polysT$Box == "Seal Island"), ]
area7=polysT[which(polysT$Box == "Scots Bay"), ]
area8=polysT[which(polysT$Box == "Yankee Bank"), ]
area9=polysT[which(polysT$Box == "Trinity"), ]
area10=polysT[which(polysT$Box == "Browns Bank"), ]
area11=polysT[which(polysT$Box == "SW Grounds"), ]
area12=polysT[which(polysT$Box == "Gannet Dry Ledge"), ]
area13=polysT[which(polysT$Box == "Lurcher"), ]


ids = (TaggingEvents$TAG_NUMBER)
r = data.frame( TAG_NUMBER=ids, 
                X = NA, 
                Y = NA, 
                NB_Coastal = NA, 
                Grand_Manan = NA, 
                Grand_Manan_Banks = NA,
                Long_Island = NA, 
                German_Bank = NA, 
                Seal_Island = NA, 
                Scots_Bay = NA,
                Yankee_Bank = NA,
                Trinity = NA,
                Browns_Bank = NA,
                SW_Grounds = NA,
                Gannet_Dry_Ledge = NA,
                Lurcher = NA) 

r <- r %>%
  left_join(TaggingEvents %>% dplyr::select(TAG_NUMBER, Lat, Lon), by = "TAG_NUMBER") %>%
  mutate(
    Y = Lat,
    X = Lon
  ) %>%
  dplyr::select(-Lat, -Lon)


r$NB_Coastal        <- point.in.polygon(r$Y, r$X, area1$Y, area1$X, mode.checked=FALSE)
r$Grand_Manan       <- point.in.polygon(r$Y, r$X, area2$Y, area2$X, mode.checked=FALSE)
r$Grand_Manan_Banks <- point.in.polygon(r$Y, r$X, area3$Y, area3$X, mode.checked=FALSE)
r$Long_Island       <- point.in.polygon(r$Y, r$X, area4$Y, area4$X, mode.checked=FALSE)
r$German_Bank       <- point.in.polygon(r$Y, r$X, area5$Y, area5$X, mode.checked=FALSE)
r$Seal_Island       <- point.in.polygon(r$Y, r$X, area6$Y, area6$X, mode.checked=FALSE)
r$Scots_Bay         <- point.in.polygon(r$Y, r$X, area7$Y, area7$X, mode.checked=FALSE)
r$Yankee_Bank       <- point.in.polygon(r$Y, r$X, area8$Y, area8$X, mode.checked=FALSE)
r$Trinity           <- point.in.polygon(r$Y, r$X, area9$Y, area9$X, mode.checked=FALSE)
r$Browns_Bank       <- point.in.polygon(r$Y, r$X, area10$Y, area10$X, mode.checked=FALSE)
r$SW_Grounds        <- point.in.polygon(r$Y, r$X, area11$Y, area11$X, mode.checked=FALSE)
r$Gannet_Dry_Ledge  <- point.in.polygon(r$Y, r$X, area12$Y, area12$X, mode.checked=FALSE)
r$Lurcher           <- point.in.polygon(r$Y, r$X, area13$Y, area13$X, mode.checked=FALSE)

r <- r %>%
  mutate(FishingGround = case_when(
    NB_Coastal > 0        ~ "NB Coastal",
    Grand_Manan > 0       ~ "Grand Manan",
    Grand_Manan_Banks > 0 ~ "Grand Manan Banks",
    Long_Island > 0       ~ "Long Island",
    German_Bank > 0       ~ "German Bank",
    Seal_Island > 0       ~ "Seal Island",
    Scots_Bay > 0         ~ "Scots Bay",
    Yankee_Bank > 0       ~ "Yankee Bank",
    Trinity > 0           ~ "Trinity",
    Browns_Bank > 0       ~ "Browns Bank", 
    SW_Grounds > 0        ~ "SW Grounds",
    Gannet_Dry_Ledge > 0  ~ "Gannet Dry Ledge",
    Lurcher > 0           ~ "Lurcher",
    TRUE                  ~ "Other"
  ))

TaggingEvents <- merge(TaggingEvents, r[, c("TAG_NUMBER", "FishingGround")], by = "TAG_NUMBER")

TagReturns <- merge(TaggingEvents, completeReturns, by = "TAG_NUMBER")

# Histogram showing average time differences between tagging in Days. Split into categories.
# Category 1 = 0 to 2 days. These should mostly be removed from analysis due to them being caught almost instantly.
# Category 2 = 3 to 10 days. This is the period that the survey window covers.
# Cat. 3 = 11 to 30 days. Rest of the first month.
# Cat. 4 = 31 to 183 days. Caught after the first month, before the 6 month mark.
# Cat. 5 = 184 to 365. Minimum time of 6 months between tagging event and being recaptured.
# Cat. 6 = 366 to 730. Caught a minimum of a year, up to two years after the tagging event.
# Cat. 7 = Anything after two years since tagging event.


TagReturns <- TagReturns %>%
  mutate(
    timeDifference = as.numeric(DATE - Date),
    category = cut(
      timeDifference,
      breaks = c(-Inf, 3, 11, 31, 184, 366, 731, 1095, Inf),
      labels = 1:8,
      right = FALSE
    ),
    category = as.numeric(as.character(category)),
    Count = 1
  ) %>%
  filter(
    timeDifference >= 0,
    !is.na(TAG_NUMBER)
  )

```

# Tag Returns {.tabset}

## Average Time Difference Across All Grounds  {.tabset .tabset-fade .tabset-pills}


```{r, results = "asis", fig.align='center', class.output= "scoll-100"}

TagReturns <- TagReturns %>%
  group_by(category) %>%
  mutate(AvgtimeDifference = mean(timeDifference)) %>%
  mutate(No.InCategory = length(category)) %>%
  mutate(timeDifferenceMin = min(timeDifference)) %>%
  mutate(timeDifferenceMax= max(timeDifference)) %>%
  mutate_if(is.numeric, format, digits = 2)

ggplot(TagReturns,(aes(x = category, fill = timeDifferenceMax))) +
          geom_histogram(binwidth=1, colour = "white", stat = "count") +
          theme(panel.background = element_rect(fill = "white", colour = "grey50")) +
          labs(x = "Category", y="Count") +
          scale_fill_discrete(breaks = c("2", "10", "30", "133", "365", "715", "1079", "2092"), name = "Maximum time difference between tag and recapture")+
          scale_x_discrete(guide = guide_axis(n.dodge = 3))

TagReturns = TagReturns %>%
  group_by(timeDifference) %>%
  mutate(No.ofSameNumberOfDays = length(timeDifference)) %>%
  mutate_if(is.numeric, format, digits = 2)


Table <- TagReturns %>%
  dplyr::select(category,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)%>%
  arrange(category)

 Table1 <- unique(Table) %>%
             arrange(category)

Table1 %>% write.csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tagging/Tag Returns/tagReturnsTracey.csv"))

SummaryTable <- subset(Table1, select = -c(timeDifference, No.ofSameNumberOfDays))
 SummaryTable <- unique(SummaryTable) %>%
   arrange(category)
 
kbl(SummaryTable, col.names=c("Category", "Average Time Difference (days)", "Minimum Time Difference (Days)", "Maximum Time Difference (Days)", "Category Abundance"), align = "c")

Cat1 <- subset(TagReturns, category == "1")
Cat1 <- subset(Cat1, subset = (catchAREA == "German Bank" |
                               catchAREA == "German Bank (Area 7)" |
                               catchAREA == "Lurcher" |
                                 catchAREA == "NB Coastal" |
                                 catchAREA =="Grand Manan" |
                                 catchAREA == "Grand Manan Banks" |
                                 catchAREA =="Long Island"|
                                 catchAREA =="Seal Island"|
                                 catchAREA == "Scots Bay"|
                                 catchAREA =="Yankee Bank"|
                                 catchAREA =="Trinity"|
                                 catchAREA =="Brown Bank"|
                                 catchAREA =="SW Grounds"|
                                 catchAREA =="Gannet Dry Ledge" ))

ggplot(data = Cat1, (aes(FishingGround, fill = catchAREA))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tagging Ground", y="Count") +
        scale_fill_discrete(name = "Recapture area")+
        scale_x_discrete(guide = guide_axis(n.dodge = 3))


```

## Scots Bay, German Bank and Seal Island Tags {.tabset .tabset-fade .tabset-pills}

### Tag Returns between German Bank and Scots Bay

```{r, results = "asis", fig.align='center'}

GBtoSB <- TagReturns %>%
  filter(
    (FishingGround == "Scots Bay"   & catchAREA %in% c("German Bank", "German Bank (Area 7)")) |
    (FishingGround == "German Bank" & catchAREA %in% c("Scots Bay",  "Scots Bay (Area 8)"))
  ) %>%
  mutate(
    TagLocation = case_when(
      FishingGround == "Scots Bay"   ~ "SB to GB",
      FishingGround == "German Bank" ~ "GB to SB",
      TRUE ~ "Other"
    ),
    timeDifference = as.numeric(timeDifference)
  )

GBSB <- GBtoSB %>%
  filter(TagLocation == "GB to SB") %>%
  group_by(category) %>%
  mutate(No.InCategory = n()) %>%
  ungroup()

SBGB <- GBtoSB %>%
  filter(TagLocation == "SB to GB") %>%
  group_by(category) %>%
  mutate(No.InCategory = n()) %>%
  ungroup()

ggplot(GBSB,
       aes(
         x = factor(category),
         y = Count,
         fill = factor(timeDifferenceMax)
       )) +
  geom_col() +
  labs(
    title = "Tag Returns that started in German Bank and were retrieved in Scots Bay",
    x = "Category",
    y = "Number of Events",
    fill = "Maximum time difference between tag and recapture"
  )

ggplot(SBGB,
       aes(
         x = factor(category),
         y = Count,
         fill = factor(timeDifferenceMax)
       )) +
  geom_col() +
  labs(
    title = "Tag Returns that started in Scots Bay and were retrieved in German Bank",
    x = "Category",
    y = "Number of Events",
    fill = "Maximum time difference between tag and recapture"
  )

create_summary_table <- function(data) {

  data %>%
    select(
      category,
      FishingGround,
      catchAREA,
      AvgtimeDifference,
      timeDifferenceMin,
      timeDifferenceMax,
      No.InCategory
    ) %>%
    distinct() %>%
    arrange(category)
}

SummaryTable_GBSB <- GBSB %>%
  dplyr::select(
    category,
    FishingGround,
    catchAREA,
    AvgtimeDifference,
    timeDifferenceMin,
    timeDifferenceMax,
    No.InCategory
  ) %>%
  distinct() %>%
  arrange(category)

kbl(
  SummaryTable_GBSB,
  col.names = c(
    "Category",
    "Initial Tagging Ground",
    "Tag Retrieval Ground",
    "Average Time from Tagging Event",
    "Minimum Time Difference",
    "Maximum Time Difference",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

SummaryTable_SBGB <- SBGB %>%
  dplyr::select(
    category,
    FishingGround,
    catchAREA,
    AvgtimeDifference,
    timeDifferenceMin,
    timeDifferenceMax,
    No.InCategory
  ) %>%
  distinct() %>%
  arrange(category)

kbl(
  SummaryTable_SBGB,
  col.names = c(
    "Category",
    "Initial Tagging Ground",
    "Tag Retrieval Ground",
    "Average Time from Tagging Event",
    "Minimum Time Difference",
    "Maximum Time Difference",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

```
### Tag returns that started in either German Bank or Scots Bay

```{r, results = "asis", fig.align='center'}

TagReturns <- TagReturns %>%
  mutate(
    TagLocation = case_when(
      FishingGround == "Scots Bay" &
        catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "SB to GB",

      FishingGround == "German Bank" &
        catchAREA %in% c("Scots Bay", "Scots Bay (Area 8)") ~ "GB to SB",

      FishingGround == "German Bank" &
        catchAREA == "German Bank" ~ "GB to GB",

      FishingGround == "Scots Bay" &
        catchAREA == "Scots Bay" ~ "SB to SB",

      FishingGround == "Scots Bay" ~ "SB to Other",

      FishingGround == "German Bank" ~ "GB to Other",

      TRUE ~ "Other"
    )
  )

TagReturns1 <- TagReturns %>%
  filter(!TagLocation %in% c("Other", "SB to Other", "GB to Other"))

TagReturns1 <- TagReturns1 %>%
  group_by(TagLocation, category) %>%
  mutate(No.InCategory = n()) %>%
  ungroup()

ggplot(TagReturns1,
       aes(x = TagLocation, fill = factor(category))) +
  geom_bar(colour = "white") +
  theme(
    panel.background = element_rect(fill = "white", colour = "grey50")
  ) +
  labs(
    x = "Tag Location",
    y = "Count",
    fill = "Category"
  ) +
  scale_y_continuous(breaks = pretty_breaks())


SummaryTable <- TagReturns1 %>%
  dplyr::select(
    category,
    FishingGround,
    catchAREA,
    AvgtimeDifference,
    timeDifferenceMin,
    timeDifferenceMax,
    No.InCategory
  ) %>%
  distinct() %>%
  arrange(category)

kbl(
  SummaryTable,
  col.names = c(
    "Category",
    "Initial Tagging Ground",
    "Tag Retrieval Ground",
    "Average Time from Tagging Event",
    "Minimum Time Difference",
    "Maximum Time Difference",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

```
### Tag Returns between German Bank and Seal Island

```{r, results = "asis", fig.align='center'}

library(dplyr)
library(ggplot2)
library(scales)
library(kableExtra)

TagReturnsGBSI <- TagReturns %>%
  filter(
    FishingGround %in% c("German Bank", "Seal Island"),
    catchAREA %in% c("German Bank", "German Bank (Area 7)", "Seal Island")
  ) %>%
  mutate(
    TagLocation = case_when(
      FishingGround == "German Bank" &
        catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "GB to GB",

      FishingGround == "German Bank" &
        catchAREA == "Seal Island" ~ "GB to SI",

      FishingGround == "Seal Island" &
        catchAREA == "Seal Island" ~ "SI to SI",

      FishingGround == "Seal Island" &
        catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "SI to GB",

      TRUE ~ "Other"
    )
  ) %>%
  filter(TagLocation %in% c("GB to SI", "SI to GB")) %>%
  group_by(TagLocation, category) %>%
  mutate(No.InCategory = n()) %>%
  ungroup()

ggplot(TagReturnsGBSI,
       aes(x = TagLocation, fill = factor(category))) +
  geom_bar(colour = "white") +
  theme(
    panel.background = element_rect(
      fill = "white",
      colour = "grey50"
    )
  ) +
  labs(
    x = "Tag Location",
    y = "Count",
    fill = "Category"
  ) +
  scale_y_continuous(breaks = pretty_breaks())

Table_GBSI <- TagReturnsGBSI %>%
  dplyr::select(
    TAG_NUMBER,
    category,
    Date,
    FishingGround,
    DATE,
    catchAREA,
    timeDifference,
    AvgtimeDifference,
    timeDifferenceMin,
    timeDifferenceMax,
    No.InCategory,
    No.ofSameNumberOfDays
  ) %>%
  arrange(timeDifference)

SummaryTable_GBSI <- Table_GBSI %>%
  dplyr::select(
    category,
    FishingGround,
    catchAREA,
    AvgtimeDifference,
    timeDifferenceMin,
    timeDifferenceMax,
    No.InCategory
  ) %>%
  distinct() %>%
  arrange(category)

kbl(
  SummaryTable_GBSI,
  col.names = c(
    "Category",
    "Initial Tagging Ground",
    "Tag Retrieval Ground",
    "Average Time from Tagging Event",
    "Minimum Time Difference",
    "Maximum Time Difference",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

```


## By Ground {.tabset .tabset-fade .tabset-pills}

### German Bank 

```{r, results = "asis", fig.align='center'}
GB <- ground_report(
  TagReturns,
  "German Bank"
)

GB$plot

kbl(
  GB$summary,
  col.names = c(
    "Time Difference",
    "Tag Location",
    "Category",
    "Abundance"
  ),
  align = "c"
) %>%
  kable_paper(
    "striped",
    full_width = FALSE
  )

# TagReturnsGB <- create_tag_returns(
#   TagReturns,
#   "German Bank"
# )
# 
# SummaryTable <- create_summary_table(
#   TagReturnsGB
# )
# 
# kbl(
#   SummaryTable,
#   col.names = c(
#     "Time Difference",
#     "Tag Location",
#     "Category",
#     "Abundance in Category"
#   ),
#   align = "c"
# ) %>%
#   kable_paper("striped", full_width = FALSE)
# 
# TagReturnsGB_noCat1 <- TagReturnsGB %>%
#   filter(category != 1)
# 
# ggplot(
#   TagReturnsGB_noCat1,
#   aes(x = TagLocation, fill = factor(category))
# ) +
#   geom_bar(colour = "white") +
#   theme(
#     panel.background = element_rect(
#       fill = "white",
#       colour = "grey50"
#     )
#   ) +
#   labs(
#     x = "Tag to Catch Location",
#     y = "Number of Events",
#     fill = "Category"
#   ) +
#   ggtitle(
#     "German Bank Tag Returns Excluding Fish Caught Within 2 Days of Tagging"
#   ) +
#   scale_y_continuous(breaks = pretty_breaks())
# 
# Table_GB <- TagReturnsGB_noCat1 %>%
#   dplyr::select(
#     TAG_NUMBER,
#     category,
#     Date,
#     FishingGround,
#     DATE,
#     catchAREA,
#     timeDifference,
#     AvgtimeDifference,
#     timeDifferenceMin,
#     timeDifferenceMax,
#     No.InCategory,
#     No.ofSameNumberOfDays
#   )
# 
# SummaryTable <- TagReturnsGB_noCat1 %>%
#   count(TagLocation, category, name = "Abundance")
# 
# kbl(
#   SummaryTable,
#   col.names = c(
#     "Time Difference", 
#     "Tag Location",
#     "Category",
#     "Abundance in Category"
#   ),
#   align = "c"
# ) %>%
#   kable_paper("striped", full_width = FALSE)

```

### NB Coastal

```{r, results = "asis", fig.align='center'}

# NB Coastal Tag Returns
TagReturnsNBC <- TagReturns %>%
  filter(FishingGround == "NB Coastal") %>%
  mutate(
    TagLocation = case_when(
      catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "NBC to GB",
      catchAREA %in% c("Scots Bay", "Scots Bay (Area 8)") ~ "NBC to SB",
      catchAREA == "NB Coastal" ~ "NBC to NBC",
      catchAREA == "Grand Manan" ~ "NBC to GM",
      catchAREA == "Grand Manan Banks" ~ "NBC to GMB",
      catchAREA == "Long Island" ~ "NBC to LI",
      catchAREA == "Seal Island" ~ "NBC to SI",
      catchAREA == "Yankee Bank" ~ "NBC to YB",
      catchAREA == "Trinity" ~ "NBC to T",
      catchAREA == "Browns Bank" ~ "NBC to BB",
      catchAREA == "SW Grounds" ~ "NBC to SWG",
      catchAREA == "Gannet Dry Ledge" ~ "NBC to GDL",
      catchAREA == "Lurcher" ~ "NBC to L",
      TRUE ~ "Other"
    )
  ) %>%
  filter(TagLocation != "Other")

SummaryTable <- TagReturnsNBC %>%
  count(TagLocation, category, name = "Abundance") %>%
  ungroup()

kbl(
  SummaryTable,
  col.names = c(
    "Time Difference",
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

TagReturnsNBC <- TagReturnsNBC %>%
  filter(category != 1)

TagReturnsNBC <- TagReturnsNBC %>%
  filter(category != "1")

ggplot(
  TagReturnsNBC,
  aes(x = TagLocation, fill = factor(category))
) +
  geom_bar(colour = "white") +
  theme(
    panel.background = element_rect(
      fill = "white",
      colour = "grey50"
    )
  ) +
  labs(
    x = "Tag to Catch Location",
    y = "Number of Events",
    fill = "Category"
  ) +
  ggtitle(
    "NB Coastal Tag Returns Excluding Fish Caught Within 2 Days of Tagging"
  ) +
  scale_y_continuous(breaks = pretty_breaks())

```

### Grand Manan

```{r, results = "asis", fig.align='center'}

# Grand Manan tag returns
TagReturnsGM <- TagReturns %>%
  filter(FishingGround == "Grand Manan") %>%
  mutate(
    TagLocation = case_when(
      catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "GM to GB",
      catchAREA %in% c("Scots Bay", "Scots Bay (Area 8)")     ~ "GM to SB",
      catchAREA == "NB Coastal"                               ~ "GM to NBC",
      catchAREA == "Grand Manan"                              ~ "GM to GM",
      catchAREA == "Grand Manan Banks"                        ~ "GM to GMB",
      catchAREA == "Long Island"                              ~ "GM to LI",
      catchAREA == "Seal Island"                              ~ "GM to SI",
      catchAREA == "Yankee Bank"                              ~ "GM to YB",
      catchAREA == "Trinity"                                  ~ "GM to T",
      catchAREA == "Browns Bank"                              ~ "GM to BB",
      catchAREA == "SW Grounds"                               ~ "GM to SWG",
      catchAREA == "Gannet Dry Ledge"                         ~ "GM to GDL",
      catchAREA == "Lurcher"                                  ~ "GM to L",
      TRUE                                                    ~ "Other"
    )
  ) %>%
  filter(TagLocation != "Other")

SummaryTable <- TagReturnsGM %>%
  count(TagLocation, category, name = "Abundance")

kbl(
  SummaryTable,
  col.names = c(
    "Time Difference",
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

TagReturnsGM <- TagReturnsGM %>%
  filter(category != 1)

ggplot(
  TagReturnsGM,
  aes(x = TagLocation, fill = factor(category))
) +
  geom_bar(colour = "white") +
  theme(
    panel.background = element_rect(
      fill = "white",
      colour = "grey50"
    )
  ) +
  labs(
    x = "Tag to Catch Location",
    y = "Number of Events",
    fill = "Category"
  ) +
  ggtitle(
    "Grand Manan Tag Returns Excluding Fish Caught Within 2 Days of Being Tagged"
  ) +
  scale_y_continuous(breaks = pretty_breaks())

SummaryTable <- TagReturnsGM %>%
  count(TagLocation, category, name = "Abundance")

kbl(
  SummaryTable,
  col.names = c(
    "Time Difference",
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

```

### Grand Manan Banks

```{r, results = "asis", fig.align='center'}

# Grand Manan Banks tag returns
TagReturnsGMB <- TagReturns %>%
  filter(FishingGround == "Grand Manan Banks") %>%
  mutate(
    TagLocation = case_when(
      catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "GMB to GB",
      catchAREA %in% c("Scots Bay", "Scots Bay (Area 8)")     ~ "GMB to SB",
      catchAREA == "NB Coastal"                               ~ "GMB to NBC",
      catchAREA == "Grand Manan"                              ~ "GMB to GM",
      catchAREA == "Grand Manan Banks"                        ~ "GMB to GMB",
      catchAREA == "Long Island"                              ~ "GMB to LI",
      catchAREA == "Seal Island"                              ~ "GMB to SI",
      catchAREA == "Yankee Bank"                              ~ "GMB to YB",
      catchAREA == "Trinity"                                  ~ "GMB to T",
      catchAREA == "Browns Bank"                              ~ "GMB to BB",
      catchAREA == "SW Grounds"                               ~ "GMB to SWG",
      catchAREA == "Gannet Dry Ledge"                         ~ "GMB to GDL",
      catchAREA == "Lurcher"                                  ~ "GMB to L",
      TRUE                                                    ~ "Other"
    )
  ) %>%
  filter(TagLocation != "Other")

SummaryTable <- TagReturnsGMB %>%
  count(TagLocation, category, name = "Abundance")

kbl(
  SummaryTable,
  col.names = c(
    "Time Difference",
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

TagReturnsGMB <- TagReturnsGMB %>%
  filter(category != 1)

TagReturnsGMB <- TagReturnsGMB %>%
  filter(category != "1")

ggplot(
  TagReturnsGMB,
  aes(x = TagLocation, fill = factor(category))
) +
  geom_bar(colour = "white") +
  theme(
    panel.background = element_rect(
      fill = "white",
      colour = "grey50"
    )
  ) +
  labs(
    x = "Tag to Catch Location",
    y = "Number of Events",
    fill = "Category"
  ) +
  ggtitle(
    "Grand Manan Banks Tag Returns Excluding Fish Caught Within 2 Days of Being Tagged"
  ) +
  scale_y_continuous(breaks = pretty_breaks())

SummaryTable <- TagReturnsGMB %>%
  count(TagLocation, category, name = "Abundance")

kbl(
  SummaryTable,
  col.names = c(
    "Time Difference",
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

```

### Long Island

```{r, results = "asis", fig.align='center'}

library(dplyr)
library(ggplot2)
library(kableExtra)
library(scales)

# Long Island tag returns
TagReturnsLI <- TagReturns %>%
  filter(FishingGround == "Long Island") %>%
  mutate(
    TagLocation = case_when(
      catchAREA %in% c("German Bank", "German Bank (Area 7)") ~ "LI to GB",
      catchAREA %in% c("Scots Bay", "Scots Bay (Area 8)")     ~ "LI to SB",
      catchAREA == "NB Coastal"                               ~ "LI to NBC",
      catchAREA == "Grand Manan"                              ~ "LI to GM",
      catchAREA == "Grand Manan Banks"                        ~ "LI to GMB",
      catchAREA == "Long Island"                              ~ "LI to LI",
      catchAREA == "Seal Island"                              ~ "LI to SI",
      catchAREA == "Yankee Bank"                              ~ "LI to YB",
      catchAREA == "Trinity"                                  ~ "LI to T",
      catchAREA == "Browns Bank"                              ~ "LI to BB",
      catchAREA == "SW Grounds"                               ~ "LI to SWG",
      catchAREA == "Gannet Dry Ledge"                         ~ "LI to GDL",
      catchAREA == "Lurcher"                                  ~ "LI to L",
      TRUE                                                    ~ "Other"
    )
  ) %>%
  filter(TagLocation != "Other")

SummaryTable <- TagReturnsLI %>%
  count(TagLocation, category, name = "Abundance")

kbl(
  SummaryTable,
  col.names = c(
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

TagReturnsLI <- TagReturnsLI %>%
  filter(category != 1)

ggplot(
  TagReturnsLI,
  aes(x = TagLocation, fill = factor(category))
) +
  geom_bar(colour = "white") +
  theme(
    panel.background = element_rect(
      fill = "white",
      colour = "grey50"
    )
  ) +
  labs(
    x = "Tag to Catch Location",
    y = "Number of Events",
    fill = "Category"
  ) +
  ggtitle(
    "Long Island Tag Returns Excluding Fish Caught Within 2 Days of Being Tagged"
  ) +
  scale_y_continuous(breaks = pretty_breaks())

SummaryTable <- TagReturnsLI %>%
  count(TagLocation, category, name = "Abundance")

kbl(
  SummaryTable,
  col.names = c(
    "Tag Location",
    "Category",
    "Abundance in Category"
  ),
  align = "c"
) %>%
  kable_paper("striped", full_width = FALSE)

```

### Seal Island

```{r, results = "asis", fig.align='center'}
TagReturnsSI <- subset(TagReturns, subset = (FishingGround == "Seal Island"))

TagReturnsSI$TagLocation <- with(TagReturnsSI, ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "German Bank" |
                                                      TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "German Bank (Area 7)", "SI to GB",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Scots Bay" |
                                                      TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Scots Bay (Area 8)", "SI to SB",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "NB Coastal", "SI to NBC",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Grand Manan", "SI to GM",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Grand Manan Banks", "SI to GMB",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Long Island", "SI to LI",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Seal Island", "SI to SI",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Yankee Bank", "SI to YB",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Trinity", "SI to T",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Browns Bank", "SI to BB",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "SW Grounds", "SI to SWG",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Gannet Dry Ledge", "SI to GDL",
                                               ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Lurcher", "SI to L", "Other"
                                                                                                                                   ))))))))))))))

TagReturnsSI <- subset(TagReturnsSI, TagLocation != "Other")

SummaryTable <- TagReturnsSI %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)


#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsSI <- subset(TagReturnsSI, subset = (category != "1"))

ggplot(data = TagReturnsSI, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Seal Island Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())


SummaryTable <- TagReturnsSI %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

```

### Scots Bay

```{r, results = "asis", fig.align='center'}
TagReturnsSB <- subset(TagReturns, subset = (FishingGround == "Scots Bay"))

TagReturnsSB$TagLocation <- with(TagReturnsSB, ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "German Bank" |
                                                        TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "German Bank (Area 7)", "SB to GB",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Scots Bay" |
                                                      TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Scots Bay (Area 8)", "SB to SB",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "NB Coastal", "SB to NBC",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Grand Manan", "SB to GM",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Grand Manan Banks", "SB to GMB",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Long Island", "SB to LI",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Seal Island", "SB to SI",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Yankee Bank", "SB to YB",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Trinity", "SB to T",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Browns Bank", "SB to BB",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "SW Grounds", "SB to SWG",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Gannet Dry Ledge", "SB to GDL",
                                               ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Lurcher", "SB to L","Other"
                                                                                                                            ))))))))))))))

TagReturnsSB <- subset(TagReturnsSB, TagLocation != "Other")

SummaryTable <- TagReturnsSB %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)


# ggplot(data = TagReturnsSB, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("Scots Bay Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())
# 
# Table <- TagReturnsSB %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsSB <- subset(TagReturnsSB, subset = (category != "1"))

ggplot(data = TagReturnsSB, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Scots Bay Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsSB %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsSB %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

```

### Yankee Bank

```{r, results = "asis", fig.align='center'}
TagReturnsYB <- subset(TagReturns, subset = (FishingGround == "Yankee Bank"))

TagReturnsYB$TagLocation <- with(TagReturnsYB, ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "German Bank" |
                                                      TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "German Bank (Area 7)", "YB to GB",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Scots Bay" |
                                                      TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Scots Bay (Area 8)", "YB to SB",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "NB Coastal", "YB to NBC",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Grand Manan", "YB to GM",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Grand Manan Banks", "YB to GMB",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Long Island", "YB to LI",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Seal Island", "YB to SI",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Yankee Bank", "YB to YB",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Trinity", "YB to T",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Browns Bank", "YB to BB",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "SW Grounds", "YB to SWG",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Gannet Dry Ledge", "YB to GDL",
                                               ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Lurcher", "YB to L", "Other"
                                                                                                                            ))))))))))))))

TagReturnsYB <- subset(TagReturnsYB, TagLocation != "Other")

SummaryTable <- TagReturnsYB %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

# ggplot(data = TagReturnsYB, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("Yankee Bank Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())
# 
# Table <- TagReturnsYB %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsYB <- subset(TagReturnsYB, subset = (category != "1"))

ggplot(data = TagReturnsYB, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Yankee Bank Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsYB %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsYB %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)


```

### Trinity

```{r, results = "asis", fig.align='center'}
TagReturnsT <- subset(TagReturns, subset = (FishingGround == "Trinity"))

TagReturnsT$TagLocation <- with(TagReturnsT, ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "German Bank" |
                                                    TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "German Bank (Area 7)", "T to GB",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Scots Bay" |
                                                    TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Scots Bay (Area 8)", "T to SB",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "NB Coastal", "T to NBC",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Grand Manan", "T to GM",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Grand Manan Banks", "T to GMB",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Long Island", "T to LI",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Seal Island", "T to SI",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Yank", "T to YB",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Trinity", "T to T",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Browns Bank", "T to BB",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "SW Grounds", "T to SWG",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Gannet Dry Ledge", "T to GDL",
                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Lurcher", "T to L","Other"
                                                                                                                            ))))))))))))))

TagReturnsT <- subset(TagReturnsT, TagLocation != "Other")

SummaryTable <- TagReturnsT %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

# ggplot(data = TagReturnsT, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("Trinity Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsT %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsT <- subset(TagReturnsT, subset = (category != "1"))

ggplot(data = TagReturnsT, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Trinity Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsT %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsT %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

```

### Browns Bank

```{r, results = "asis", fig.align='center'}
TagReturnsBB <- subset(TagReturns, subset = (FishingGround == "Browns Bank"))

TagReturnsBB$TagLocation <- with(TagReturnsBB, ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "German Bank" |
                                                      TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "German Bank (Area 7)", "BB to GB",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Scots Bay" |
                                                      TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Scots Bay (Area 8)", "BB to SB",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "NB Coastal", "BB to NBC",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Grand Manan", "BB to GM",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Grand Manan Banks", "BB to GMB",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Long Island", "BB to LI",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Seal Island", "BB to SI",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Yank", "BB to YB",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Trinity", "BB to T",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Browns Bank", "BB to BB",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "SW Grounds", "BB to SWG",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Gannet Dry Ledge", "BB to GDL",
                                               ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Lurcher", "BB to L", "Other"
                                                                                                                          ))))))))))))))


TagReturnsBB <- subset(TagReturnsBB, TagLocation != "Other")

SummaryTable <- TagReturnsBB %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

# ggplot(data = TagReturnsBB, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("Browns Bank Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())
# 
# Table <- TagReturnsBB %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsBB <- subset(TagReturnsBB, subset = (category != "1"))

ggplot(data = TagReturnsBB, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Browns Bank Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsBB %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsBB %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

### SW Ground

```{r, results = "asis", fig.align='center'}
TagReturnsSWG <- subset(TagReturns, subset = (FishingGround == "SW Grounds"))

TagReturnsSWG$TagLocation <- with(TagReturnsSWG, ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "German Bank" |
                                                        TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "German Bank (Area 7)", "SWG to GB",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Scots Bay" |
                                                        TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Scots Bay (Area 8)", "SWG to SB",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "NB Coastal", "SWG to NBC",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Grand Manan", "SWG to GM",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Grand Manan Banks", "SWG to GMB",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Long Island", "SWG to LI",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Seal Island", "SWG to SI",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Yank", "SWG to YB",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Trinity", "SWG to T",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Browns Bank", "SWG to BB",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "SW Grounds", "SWG to SWG",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Gannet Dry Ledge", "SWG to GDL",
                                                 ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Lurcher", "GDL to L","Other"
                                                                                                                            ))))))))))))))

TagReturnsSWG <- subset(TagReturnsSWG, TagLocation != "Other")

SummaryTable <- TagReturnsSWG %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

# ggplot(data = TagReturnsSWG, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("SW Grounds Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsSWG %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.
#Not sure why an NA has popped up

TagReturnsSWG <- subset(TagReturnsSWG, subset = (category != "1"))

ggplot(data = TagReturnsSWG, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("SW Grounds Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsSWG %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsSWG %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)
```

### Gannet Dry Ledge

```{r, results = "asis", fig.align='center'}
TagReturnsGDL <- subset(TagReturns, subset = (FishingGround == "Gannet Dry Ledge"))

TagReturnsGDL$TagLocation <- with(TagReturnsGDL, ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "German Bank" |
                                                        TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "German Bank (Area 7)", "GDL to GB",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Scots Bay" |
                                                        TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Scots Bay (Area 8)", "GDL to SB",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "NB Coastal", "GDL to NBC",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Grand Manan", "GDL to GM",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Grand Manan Banks", "GDL to GMB",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Long Island", "GDL to LI",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Seal Island", "GDL to SI",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Yank", "GDL to YB",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Trinity", "GDL to T",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Browns Bank", "GDL to BB",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "SW Grounds", "GDL to SWG",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Gannet Dry Ledge", "GDL to GDL",
                                                 ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Lurcher", "GDL to L","Other"
                                                                                                                              ))))))))))))))


TagReturnsGDL <- subset(TagReturnsGDL, TagLocation != "Other")

SummaryTable <- TagReturnsGDL %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

# ggplot(data = TagReturnsGDL, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("Gannet Dry Ledge Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsGDL %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)


# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)




#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsGDL <- subset(TagReturnsGDL, subset = (category != "1"))

ggplot(data = TagReturnsGDL, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Gannet Dry Ledget Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsGDL %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)


# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsGDL %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

```

### Lurcher

```{r, results = "asis", fig.align='center'}
TagReturnsL <- subset(TagReturns, subset = (FishingGround == "Lurcher"))

TagReturnsL$TagLocation <- with(TagReturnsL, ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "German Bank" |
                                                    TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "German Bank (Area 7)", "L to GB",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Scots Bay" |
                                                    TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Scots Bay (Area 8)", "L to SB",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "NB Coastal", "L to NBC",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Grand Manan", "L to GM",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Grand Manan Banks", "L to GMB",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Long Island", "L to LI",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Seal Island", "L to SI",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Yank", "L to YB",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Trinity", "L to T",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Browns Bank", "L to BB",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "SW Grounds", "L to SWG",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Gannet Dry Ledge", "L to GDL",
                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Lurcher", "L to L", "Other"
                                                                                                                              ))))))))))))))


TagReturnsL <- subset(TagReturnsL, TagLocation != "Other")

SummaryTable <- TagReturnsL %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

# ggplot(data = TagReturnsL, (aes(TagLocation, fill = category))) + 
#         geom_histogram(binwidth=1, colour = "white", stat = "count") + 
#         theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
#         labs(x = "Tag to Catch Location", y="Number of Events") +
#         ggtitle("Lurcher Tag Returns") +
#         scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsL %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsL <- subset(TagReturnsL, subset = (category != "1"))

ggplot(data = TagReturnsL, (aes(TagLocation, fill = category))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Tag to Catch Location", y="Number of Events") +
        ggtitle("Lurcher Tag Returns excluding fish caught within 2 days of being tagged") +
        scale_y_continuous(breaks= pretty_breaks())

# Table <- TagReturnsL %>% 
#   dplyr::select(TAG_NUMBER,
#                 category,
#                 Date,
#                 FishingGround,
#                 DATE,
#                 catchAREA,
#                 timeDifference,
#                 AvgtimeDifference,
#                 timeDifferenceMin,
#                 timeDifferenceMax,
#                 No.InCategory,
#                 No.ofSameNumberOfDays)%>%
#   arrange(timeDifference)
# 
# 
# kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
#   kable_paper("striped", full_width = F)

SummaryTable <- TagReturnsL %>%
  group_by(TagLocation, category) %>%
  count()

kbl(SummaryTable, col.names = c("Tag Location", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

```

## Gear Types {.tabset .tabset-fade .tabset-pills}

### All Gear

```{r, results = "asis", fig.align='center'}

GearTable <- TagReturns %>% 
  dplyr::select(TAG_NUMBER,
                category,
                Date,
                FishingGround,
                DATE,
                catchAREA,
                GearType,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)%>%
  arrange(timeDifference)

GearTable$Count = 1
GearTable<-subset(GearTable, subset = (GearType != "N/A"))

ggplot(GearTable, aes(x=GearType, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Gear Type") +
  ggtitle("Tag Return") +
  labs(fill = "Category") +
  scale_x_discrete(guide = guide_axis(n.dodge = 3))

GearWithout1 <- subset(GearTable, subset = (category != 1))

ggplot(GearWithout1, aes(x=GearType, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Gear Type") +
  ggtitle("Tag Return") +
  labs(fill = "Category")+
  scale_x_discrete(guide = guide_axis(n.dodge = 3))

SummaryTable <- GearWithout1 %>%
  group_by(GearType, category) %>%
  count()

kbl(SummaryTable, col.names = c("Gear Type", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)


```

### Removal of Purse Seine 

```{r, results = "asis", fig.align='center'}

WeirTable <- subset(GearTable, subset = (GearType != "Purse Seine"))
WeirTable <- subset(WeirTable, subset = (GearType != "Mid Water Trawl"))
WeirTable <- subset(WeirTable, subset = (GearType != "Purse Seine/Frozen"))

ggplot(WeirTable, aes(x=GearType, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Gear Type") +
  ggtitle("Tag Return to Gear Type") +
  labs(fill = "Category")

ggplot(WeirTable, aes(x=GearType, y = Count, fill = factor(FishingGround))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Gear Type") +
  ggtitle("Tag Return to gear type from specific tagging ground") +
  labs(fill = "Tagging Ground")

SummaryTable <-WeirTable %>%
  group_by(GearType, category) %>%
  count()

kbl(SummaryTable, col.names = c("Gear Type", "Category", "Abundance in Category"), align = "c") %>%
  kable_paper("striped", full_width = F)

```
