---
title: "Survey Factors"
output: html_document
date: "2024-04-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#ANOVA Survey Factors Investigations_Scots Bay Tides

library(rlang)
library(cli)
library(lubridate)
library(reprex)
library(tidyverse)
library(geosphere)
library(reshape2)
library(moderndive)
library(skimr)
library(ggridges)
library(weathercan)
library(GGally)
library(psych)
library(sp)
library(raster)
library(PBSmapping)
library(rgeos) # replaced by terra and sf
library(knitr)
library(kableExtra)
library(grid)
library(gridExtra)
library(cowplot)
library(readxl)
library(hms)
library(measurements)
library(ggplot2)
library(maps)
library(dplyr)
library(RColorBrewer)
library(AICcmodavg)
library(datasets)
library(terra)
library(multcompView)
library(sf)
library(zoo)
library(ggrepel)
library(tidyr)

###remove everything in environment
rm(list = ls())
options(scipen = 999)

setwd("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Source Data/Survey Factors")

Survey_Factors <- read_csv("surveyFactorsAll_Tracey with SSB data.csv")
Survey_Factors$Julian = as.POSIXlt(Survey_Factors$Survey_Date)$yday

SSBEstimates <- read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/SSB Estimates.csv")
Survey_Data <- read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/Survey Data.csv")

#Need to find a way to import sunset and tide times


RollingPeakBiomassAvg <- read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Tracey's Folder/RollingPeakBiomassAvg.csv")
RollingPeakBiomassAvgGB <- read_csv("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Tracey's Folder/RollingPeakBiomassAvgGB.csv")

```

# Scots Bay Julian and Biomass

```{r, echo=FALSE}

ScotsBay_Turnover <- Survey_Factors %>%
  dplyr::select(Survey_Date, Ground, Julian, DFO_Estimate) %>%
  na.omit() %>%
  filter(Ground == "SB")

print(ggplot(ScotsBay_Turnover, aes(Julian, DFO_Estimate)) +
  geom_point() +
  geom_smooth(span = 1) +
  labs(
    x = "Julian Day",
    y = "Survey Biomass (mt)"
  ))

summary(aov(DFO_Estimate ~ Julian, data = ScotsBay_Turnover))


```

# Number of Vessels and biomass

```{r, echo=FALSE}

library(dplyr)

SBVesselsBiomass <- Survey_Factors %>%
  filter(
    Ground == "SB") %>%
  dplyr::select(
    Survey_Date,
    No_of_Vessels,
    Julian,
    DFO_Estimate,
    Ground
  ) %>%
  na.omit() %>%
  mutate(
    No_of_Vessels = factor(No_of_Vessels)
  )

boxplot(
  DFO_Estimate ~ No_of_Vessels,
  data = SBVesselsBiomass,
  xlab = "Number of Vessels in Survey",
  ylab = "Survey Biomass (mt)"
)

summary(
  aov(
    DFO_Estimate ~ No_of_Vessels,
    data = SBVesselsBiomass
  )
)

```

# Scots Bay Survey Area, Julian, Survey Time, High Tide Time, Survey Biomass

``` {r, echo = FALSE}

ScotsBayHighTideBiomass <- na.omit(
  subset(
    Survey_Factors,
    Ground == "SB",
    select = c(
      Survey_Date,
      No_of_Vessels,
      Ground,
      Year,
      Julian,
      DFO_Estimate,
      Survey_Start,
      High_Tide,
      Tide_Difference,
      Tide_Relative
    )
  )
)

ScotsBayHighTideBiomass$Tide_Relative <-
  as.numeric(ScotsBayHighTideBiomass$Tide_Relative)

ggplot(
  ScotsBayHighTideBiomass,
  aes(x = Tide_Relative, y = DFO_Estimate)
) +
  geom_point() +
  geom_smooth(span = 1) +
  geom_hline(
    yintercept = mean(ScotsBayHighTideBiomass$DFO_Estimate)
  ) +
  labs(
    x = "Tide Relative to Survey Start (hours)",
    y = "Survey Biomass (mt)"
  )

summary(
  aov(
    DFO_Estimate ~ Tide_Relative,
    data = ScotsBayHighTideBiomass
  )
)

```

# Scots Bay Sunset Relative

``` {r, echo = FALSE}
ScotsBaySunsetData <- na.omit(
  subset(
    Survey_Factors,
    Ground == "SB",
    select = c(
      Survey_Date,
      Year,
      Ground,
      DFO_Estimate,
      Sunset_Relative
    )
  )
)

ScotsBaySunsetData$Sunset_Relative <-
  as.numeric(ScotsBaySunsetData$Sunset_Relative)

ggplot(
  ScotsBaySunsetData,
  aes(x = Sunset_Relative, y = DFO_Estimate)
) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    x = "Sunset Relative to Survey Start (hrs)",
    y = "Survey Biomass (mt)"
  )

summary(
  lm(
    DFO_Estimate ~ Sunset_Relative,
    data = ScotsBaySunsetData
  )
)
```

###Scots Bay Peak Biomass

``` {r, echo = FALSE}

ScotsBayPeakBiomass <- Survey_Factors %>%
  dplyr::select(
    Survey_Date,
    Year,
    Julian,
    Ground,
    DFO_Turnover_Adjusted
  ) %>%
  na.omit() %>%
  filter(Ground == "SB") %>%
  group_by(Year) %>%
  slice_max(
    DFO_Turnover_Adjusted,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup() %>%
  mutate(
    Month = factor(
      format(Survey_Date, "%B"),
      levels = c(
        "June",
        "July",
        "August",
        "September"
      )
    )
  )

ggplot(
  ScotsBayPeakBiomass,
  aes(
    x = Julian,
    y = DFO_Turnover_Adjusted,
    color = Month
  )
) +
  geom_point(size = 3) +
  geom_label_repel(aes(label = Year), nudge_x = 2) +
  labs(
    x = "Julian Day",
    y = "Peak Survey Biomass (mt)",
    color = "Month"
  )

summary(
  lm(
    DFO_Turnover_Adjusted ~ Year,
    data = ScotsBayPeakBiomass
  )
)

```

### Scots Bay Index trend

``` {r, echo = FALSE}

# Total biomass by year
aggregateSB <- Survey_Factors %>%
  filter(Ground == "SB") %>%
  dplyr::select(Year, DFO_Estimate) %>%
  na.omit() %>%
  group_by(Year) %>%
  summarise(
    Total_Biomass = sum(DFO_Estimate),
    .groups = "drop"
  )

ggplot(aggregateSB, aes(Year, Total_Biomass)) +
  geom_point() +
  geom_line() +
  labs(
    x = "Year",
    y = "Total Biomass (mt)"
  )

# Peak biomass by year
ScotsBayPeakBiomass <- Survey_Factors %>%
  filter(
    Ground == "SB"
  ) %>%
  dplyr::select(Survey_Date, Year, DFO_Estimate) %>%
  na.omit() %>%
  group_by(Year) %>%
  slice_max(
    DFO_Estimate,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup()

ggplot(ScotsBayPeakBiomass,
       aes(Year, DFO_Estimate)) +
  geom_point() +
  geom_line() +
  labs(
    x = "Year",
    y = "Peak Biomass (mt)"
  )

# Combined plot
CombinedPlot <- aggregateSB %>%
  left_join(
    ScotsBayPeakBiomass %>%
      dplyr::select(Year, Peak_Biomass = DFO_Estimate),
    by = "Year"
  )

ggplot(CombinedPlot, aes(x = Year)) +
  geom_line(
    aes(
      y = Total_Biomass,
      color = "Total Biomass"
    )
  ) +
  geom_line(
    aes(
      y = Peak_Biomass,
      color = "Peak Biomass"
    )
  ) +
  geom_point(
    aes(
      y = Total_Biomass,
      color = "Total Biomass"
    )
  ) +
  geom_point(
    aes(
      y = Peak_Biomass,
      color = "Peak Biomass"
    )
  ) +
  labs(
    x = "Year",
    y = "Biomass (mt)",
    color = ""
  )

# TotalBiomass <- subset(Survey_Factors, select = c("id", "Year","Ground", "DFO_Estimate", "DFO_Turnover_Adjusted", "Survey_Date"))
#   TotalBiomass <- na.omit(TotalBiomass)
# 
# ScotsBayTotalBiomass <- subset(TotalBiomass, Ground == "SB")
#   ScotsBayTotalBiomass <- ScotsBayTotalBiomass %>% group_by(Year) %>% add_count(Year)
# aggregateSB <- aggregate(ScotsBayTotalBiomass$DFO_Estimate, list(ScotsBayTotalBiomass$Year), FUN=(sum))
# colnames(aggregateSB)<-c("Year", "DFO_Estimate")
# 
# SBTotalBiomass <- print(ggplot(aggregateSB, aes(x=Year, y=DFO_Estimate, col = "Yearly Total Biomass")) + 
#                           geom_point() +
#                           geom_line()+
#                           labs(x = "Year", y= "Total Biomass (mt)"))                    
# 
# PeakBiomass <- subset(Survey_Factors, select = c("Survey_Date", "Year","Ground", "DFO_Estimate"))
#   PeakBiomass <- na.omit(PeakBiomass)
#   PeakBiomass <- subset(PeakBiomass, Survey_Date < '2023-05-22')  
# 
# ScotsBayPeakBiomass <- subset(PeakBiomass, Ground == "SB")  
#   ScotsBayPeakBiomass <- ScotsBayPeakBiomass %>% group_by(Year) %>% slice_max(DFO_Estimate)
# 
# ggplot(ScotsBayPeakBiomass, aes(x=Year, y=DFO_Estimate, col = "Yearly Peak Biomass")) +
#   geom_point()+
#   geom_line() +
#   labs(x="Year", y="Peak Biomass (mt)")
# 
# CombinedPlot <- merge(aggregateSB, ScotsBayPeakBiomass, by="Year" )
# 
# ggplot(CombinedPlot, aes(x=Year)) + 
#           geom_line(aes(y=DFO_Estimate.x, color = "Scots Bay Total Yearly Biomass")) + 
#           geom_line(aes(y=DFO_Estimate.y, color = "Scots Bay Peak Biomass")) +
#           labs(x = "Year", y = "Total Biomass (mt)")
```

# Scots Bay 3 year rolling averages

``` {r, echo = FALSE}

ThreeYearRollingBiomass <- Survey_Factors %>%
  filter(Ground == "SB") %>%
  dplyr::select(Year, DFO_Turnover_Adjusted) %>%
  na.omit() %>%
  group_by(Year) %>%
  summarise(
    Total_Biomass = sum(DFO_Turnover_Adjusted),
    .groups = "drop"
  ) %>%
  arrange(Year) %>%
  mutate(
    RollingBiomassAvg = rollmean(
      Total_Biomass,
      k = 3,
      fill = NA,
      align = "right"
    )
  )

ggplot(
  ThreeYearRollingBiomass,
  aes(x = Year, y = RollingBiomassAvg)
) +
  geom_point() +
  geom_line() +
  labs(
    x = "Year",
    y = "Three-Year Rolling Average Biomass (mt)",
    title = "Scots Bay"
  )

```

###German Bank Julian Date and Survey Biomass

``` {r, echo = FALSE}  

GermanBankTurnover <- na.omit(
  subset(
    Survey_Factors,
    Ground == "GB",
    select = c(
      Survey_Date,
      Ground,
      Julian,
      DFO_Estimate
    )
  )
)

ggplot(
  GermanBankTurnover,
  aes(x = Julian, y = DFO_Estimate)
) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    x = "Julian Day",
    y = "Survey Biomass (mt)"
  )

summary(
  lm(
    DFO_Estimate ~ Julian,
    data = GermanBankTurnover
  )
)
  
```

### German Bank Number of Vessels and Survey Biomass
``` {r, echo = FALSE}
GBVesselsBiomass <- Survey_Factors %>%
  filter(
    Ground == "GB"
  ) %>%
  dplyr::select(
    Survey_Date,
    No_of_Vessels,
    Julian,
    DFO_Estimate,
    Ground
  ) %>%
  na.omit() %>%
  mutate(
    No_of_Vessels = factor(No_of_Vessels)
  )

boxplot(
  DFO_Estimate ~ No_of_Vessels,
  data = GBVesselsBiomass,
  xlab = "Number of Vessels in Survey",
  ylab = "Survey Biomass (mt)"
)

summary(
  aov(
    DFO_Estimate ~ No_of_Vessels,
    data = GBVesselsBiomass
  )
)
```

###German Bank Survey Area, Julian, Survey Time, High Tide Time, DFO_Estimate

``` {r, echo = FALSE}

GermanBankHighTideBiomass <- Survey_Factors %>%
  dplyr::filter(
    Ground == "GB",
   # !DFO_Estimate %in% c(228870, 191802, 143937)
  ) %>%
  dplyr::select(
    Survey_Date,
    No_of_Vessels,
    Ground,
    Year,
    Julian,
    DFO_Estimate,
    Survey_Start,
    High_Tide,
    Tide_Difference,
    Tide_Relative
  ) %>%
  na.omit()

GermanBankHighTideBiomass$Tide_Relative <-
  as.numeric(GermanBankHighTideBiomass$Tide_Relative)

ggplot(
  GermanBankHighTideBiomass,
  aes(x = Tide_Relative, y = DFO_Estimate)
) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  geom_hline(
    yintercept = mean(GermanBankHighTideBiomass$DFO_Estimate),
    linetype = "dashed"
  ) +
  labs(
    x = "Tide Relative to Survey Start (hrs)",
    y = "Survey Biomass (mt)"
  )

summary(
  lm(
    DFO_Estimate ~ Tide_Relative,
    data = GermanBankHighTideBiomass
  )
)
```

###Sunset Relative

``` {r, echo = FALSE}


ggplot(
  GermanBankSunsetData,
  aes(x = Sunset_Relative, y = DFO_Estimate)
) +
  geom_point() +
  geom_smooth(span = 1) +
  labs(
    x = "Sunset Relative to Survey Start (hrs)",
    y = "Survey Biomass (mt)"
  )

summary(
  lm(
    DFO_Estimate ~ Sunset_Relative,
    data = GermanBankSunsetData
  )
)
```

###German Bank Peak Biomass

``` {r, echo = FALSE}

GermanBankPeakBiomass <- na.omit(
  subset(
    Survey_Factors,
    Ground == "GB" &
      Survey_Date < as.Date("2023-05-22"),
    select = c(
      Survey_Date,
      Year,
      Julian,
      Ground,
      DFO_Turnover_Adjusted
    )
  )
) %>%
  group_by(Year) %>%
  slice_max(
    DFO_Turnover_Adjusted,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup()

GermanBankPeakBiomass$Month <- factor(
  format(GermanBankPeakBiomass$Survey_Date, "%B"),
  levels = c("August", "September", "October")
)

ggplot(
  GermanBankPeakBiomass,
  aes(
    x = Julian,
    y = DFO_Turnover_Adjusted,
    color = Month
  )
) +
  geom_point(size = 3) +
  geom_label_repel(aes(label = Year), nudge_x = 2) +
  labs(
    x = "Julian Day",
    y = "Peak Survey Biomass (mt)"
  )

summary(
  lm(
    DFO_Turnover_Adjusted ~ Year,
    data = GermanBankPeakBiomass
  )
)

```

### German Bank Index trend

``` {r, echo = FALSE}  

# Annual total biomass
aggregateGB <- Survey_Factors %>%
  filter(
    Ground == "GB"
  ) %>%
  dplyr::select(Year, DFO_Turnover_Adjusted) %>%
  na.omit() %>%
  group_by(Year) %>%
  summarise(
    Total_Biomass = sum(DFO_Turnover_Adjusted),
    .groups = "drop"
  )

ggplot(aggregateGB, aes(Year, Total_Biomass)) +
  geom_point() +
  geom_line() +
  labs(
    x = "Year",
    y = "Total Biomass (mt)"
  )

# Annual peak biomass
GermanBankPeakBiomass <- Survey_Factors %>%
  filter(
    Ground == "GB"
  ) %>%
  dplyr::select(
    Survey_Date,
    Year,
    DFO_Estimate
  ) %>%
  na.omit() %>%
  group_by(Year) %>%
  slice_max(
    DFO_Estimate,
    n = 1,
    with_ties = FALSE
  ) %>%
  ungroup()

ggplot(
  GermanBankPeakBiomass,
  aes(Year, DFO_Estimate)
) +
  geom_point() +
  geom_line() +
  labs(
    x = "Year",
    y = "Peak Biomass (mt)"
  )

# Combined plot
CombinedPlot <- aggregateGB %>%
  left_join(
    GermanBankPeakBiomass %>%
      dplyr::select(
        Year,
        Peak_Biomass = DFO_Estimate
      ),
    by = "Year"
  )

ggplot(CombinedPlot, aes(x = Year)) +
  geom_line(
    aes(
      y = Total_Biomass,
      color = "Total Biomass"
    )
  ) +
  geom_point(
    aes(
      y = Total_Biomass,
      color = "Total Biomass"
    )
  ) +
  geom_line(
    aes(
      y = Peak_Biomass,
      color = "Peak Biomass"
    )
  ) +
  geom_point(
    aes(
      y = Peak_Biomass,
      color = "Peak Biomass"
    )
  ) +
  labs(
    x = "Year",
    y = "Biomass (mt)",
    color = ""
  )

```

#German Bank 3 year rolling averages

``` {r, echo = FALSE}

GBData <- Survey_Factors %>%
  filter(
    Ground == "GB"
  ) %>%
  dplyr::select(
    Year,
    Survey_Date,
    DFO_Estimate,
    DFO_Turnover_Adjusted
  ) %>%
  na.omit()

ThreeYearRollingBiomass <- GBData %>%
  group_by(Year) %>%
  summarise(
    TotalBiomass = sum(DFO_Turnover_Adjusted),
    .groups = "drop"
  ) %>%
  arrange(Year) %>%
  mutate(
    AverageBiomassSumRollover = rollmean(
      TotalBiomass,
      k = 3,
      fill = NA,
      align = "right"
    )
  )

RollingPeakBiomassAvgGB <- GBData %>%
  group_by(Year) %>%
  summarise(
    PeakBiomass = max(DFO_Turnover_Adjusted),
    .groups = "drop"
  ) %>%
  arrange(Year) %>%
  mutate(
    RollingPeakBiomassAvg = rollmean(
      PeakBiomass,
      k = 3,
      fill = NA,
      align = "right"
    )
  )

CombinedPlot3 <- left_join(
  ThreeYearRollingBiomass,
  RollingPeakBiomassAvgGB,
  by = "Year"
)

ggplot(CombinedPlot3, aes(x = Year)) +
  geom_line(
    aes(
      y = AverageBiomassSumRollover,
      colour = "3-Year Rolling Total Biomass"
    )
  ) +
  geom_point(
    aes(
      y = AverageBiomassSumRollover,
      colour = "3-Year Rolling Total Biomass"
    )
  ) +
  geom_line(
    aes(
      y = RollingPeakBiomassAvg,
      colour = "3-Year Rolling Peak Biomass"
    )
  ) +
  geom_point(
    aes(
      y = RollingPeakBiomassAvg,
      colour = "3-Year Rolling Peak Biomass"
    )
  ) +
  labs(
    title = "German Bank",
    x = "Year",
    y = "Biomass (mt)",
    colour = ""
  ) +
  theme_bw()

```