---
title: "tagReturnsTracey Markdown"
output: html_document
date: "2024-04-05"
---

```{r setup, include=FALSE}
year= substr(Sys.Date(),1,4)
knitr::opts_knit$set(root.dir = paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/"))
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, fig.align='center')
```

## Data Import

```{r Data Import, include=FALSE}

completeReturns <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tag Returns/complete.returns.csv"))
TaggingEvents <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/TaggingEvents.csv"))
    TaggingEvents <- TaggingEvents %>%  
        rename(TAG_NUMBER = Tag_Num)
rawReturn <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tag Returns/rawReturn.csv"))
relINFO <- read_csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tag Returns/relINFO.csv"))
polysNAFO <- read_csv(paste0("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/NAFO_subunits.csv"))
polysT <- read_csv(paste0("C:/Users/herri/Documents/GitHub/HerringScience.github.io/Main Data/timGrounds.csv"))

                           
#Combining complete Returns and Tagging events by tag number
TagReturns <- merge(TaggingEvents, completeReturns, by = "TAG_NUMBER")




# Assigning of Grounds

area1=polysT[which(polysT$Box == "NB Coastal"), ]
area2=polysT[which(polysT$Box == "Grand Manan"), ]
area3=polysT[which(polysT$Box == "Grand Manan Banks"), ]
area4=polysT[which(polysT$Box == "Long Island"), ]
area5=polysT[which(polysT$Box == "German Bank"), ]
area6=polysT[which(polysT$Box == "Seal Island"), ]
area7=polysT[which(polysT$Box == "Scots Bay"), ]
area8=polysT[which(polysT$Box == "Yankee Bank"), ]
area9=polysT[which(polysT$Box == "Trinity"), ]
area10=polysT[which(polysT$Box == "Browns Bank"), ]
area11=polysT[which(polysT$Box == "SW Grounds"), ]
area12=polysT[which(polysT$Box == "Gannet Dry Ledge"), ]
area13=polysT[which(polysT$Box == "Lurcher"), ]


ids = (TaggingEvents$TAG_NUMBER)
r = data.frame( TAG_NUMBER=ids, 
                X = NA, 
                Y = NA, 
                NB_Coastal = NA, 
                Grand_Manan = NA, 
                Grand_Manan_Banks = NA,
                Long_Island = NA, 
                German_Bank = NA, 
                Seal_Island = NA, 
                Scots_Bay = NA,
                Yankee_Bank = NA,
                Trinity = NA,
                Browns_Bank = NA,
                SW_Grounds = NA,
                Gannet_Dry_Ledge = NA,
                Lurcher = NA) 



# Assigning fishing grounds to sets. This takes  a few minutes to run through.
for (i in 1:nrow(r)){
  test = which(TaggingEvents$TAG_NUMBER==r[i, "TAG_NUMBER"])
  test1 = TaggingEvents[test, ]
  r$Y[i] = test1$Lat
  r$X[i] = test1$Lon
  r$NB_Coastal[i] = point.in.polygon(r$Y[i], r$X[i], area1$Y, area1$X, mode.checked=FALSE)
  r$Grand_Manan[i] = point.in.polygon(r$Y[i], r$X[i], area2$Y, area2$X, mode.checked=FALSE)
  r$Grand_Manan_Banks[i] = point.in.polygon(r$Y[i], r$X[i], area3$Y, area3$X, mode.checked=FALSE)
  r$Long_Island[i] = point.in.polygon(r$Y[i], r$X[i], area4$Y, area4$X, mode.checked=FALSE)
  r$German_Bank[i] = point.in.polygon(r$Y[i], r$X[i], area5$Y, area5$X, mode.checked=FALSE)
  r$Seal_Island[i] = point.in.polygon(r$Y[i], r$X[i], area6$Y, area6$X, mode.checked=FALSE)
  r$Scots_Bay[i] = point.in.polygon(r$Y[i], r$X[i], area7$Y, area7$X, mode.checked=FALSE)
  r$Yankee_Bank[i] = point.in.polygon(r$Y[i], r$X[i], area8$Y, area8$X, mode.checked=FALSE)
  r$Trinity[i] = point.in.polygon(r$Y[i], r$X[i], area9$Y, area9$X, mode.checked=FALSE)
  r$Browns_Bank[i] = point.in.polygon(r$Y[i], r$X[i], area10$Y, area10$X, mode.checked=FALSE)
  r$SW_Grounds[i] = point.in.polygon(r$Y[i], r$X[i], area11$Y, area11$X, mode.checked=FALSE)
  r$Gannet_Dry_Ledge[i] = point.in.polygon(r$Y[i], r$X[i], area12$Y, area12$X, mode.checked=FALSE)
  r$Lurcher[i] = point.in.polygon(r$Y[i], r$X[i], area13$Y, area13$X, mode.checked=FALSE)
  
}


# Ground                        
r$FishingGround = NA        
         
r$FishingGround = with(r, ifelse(r$NB_Coastal > 0, "NB Coastal",
                                 ifelse(r$Grand_Manan > 0, "Grand Manan",
                                        ifelse(r$Grand_Manan_Banks > 0, "Grand Manan Banks",
                                               ifelse(r$Long_Island > 0, "Long Island", 
                                                      ifelse(r$German_Bank > 0, "German Bank", 
                                                             ifelse(r$Seal_Island > 0, "Seal Island",
                                                                    ifelse(r$Scots_Bay > 0, "Scots Bay",
                                                                           ifelse(r$Yankee_Bank > 0, "Yankee Bank",
                                                                                  ifelse(r$Trinity > 0, "Trinity",
                                                                                         ifelse(r$Browns_Bank > 0, "Brown Bank",
                                                                                                ifelse(r$SW_Grounds > 0, "SW Grounds",
                                                                                                       ifelse(r$Gannet_Dry_Ledge > 0, "Gannet Dry Ledge",
                                                                                                              ifelse(r$Lurcher > 0, "Lurcher", "Other"))))))))))))))
TaggingEvents <- merge(TaggingEvents, r[, c("TAG_NUMBER", "FishingGround")], by = "TAG_NUMBER")
#TaggingSubset <- TaggingEvents[sample(1:nrow(TaggingEvents), 25, replace = FALSE),]



#Combining complete Returns and Tagging events by tag number
TagReturns <- merge(TaggingEvents, completeReturns, by = "TAG_NUMBER")

# Histogram showing average time differences between tagging in Days. Split into categories.
# Category 1 = 0 to 2 days. These should mostly be removed from analysis due to them being caught almost instantly.
# Category 2 = 3 to 10 days. This is the period that the survey window covers.
# Cat. 3 = 11 to 30 days. Rest of the first month.
# Cat. 4 = 31 to 183 days. Caught after the first month, before the 6 month mark.
# Cat. 5 = 184 to 365. Minimum time of 6 months between tagging event and being recaptured.
# Cat. 6 = 366 to 730. Caught a minimum of a year, up to two years after the tagging event.
# Cat. 7 = Anything after two years since tagging event.

TagReturns$timeDifference <- TagReturns$DATE - TagReturns$Date
  TagReturns$timeDifference <- as.numeric(TagReturns$timeDifference)
  TagReturns <- TagReturns[TagReturns$timeDifference >= 0,]
TagReturns$category = with(TagReturns, ifelse(TagReturns$timeDifference < 3, 1,
                                              ifelse(TagReturns$timeDifference < 11 & TagReturns$timeDifference >= 3, 2,
                                                     ifelse(TagReturns$timeDifference < 31 & TagReturns$timeDifference >= 11, 3,
                                                            ifelse(TagReturns$timeDifference < 184 & TagReturns$timeDifference >= 31, 4,
                                                                   ifelse(TagReturns$timeDifference < 366 & TagReturns$timeDifference >= 184, 5,
                                                                          ifelse(TagReturns$timeDifference < 731 & TagReturns$timeDifference >= 366, 6,
                                                                                 ifelse(TagReturns$timeDifference < 1095 & TagReturns$timeDifference >= 731, 7, 8))))))))
                                                   
  
TagReturns$category <- as.numeric(TagReturns$category)

```

## Including Plots

```{r pressure, echo=FALSE}
TagReturns = TagReturns %>%
  group_by(category) %>%
  mutate(AvgtimeDifference = mean(timeDifference)) %>%
  mutate(No.InCategory = length(category)) %>%
  mutate(timeDifferenceMin =min(timeDifference)) %>%
  mutate(timeDifferenceMax= max(timeDifference)) %>%
  mutate_if(is.numeric, format, digits = 2)

TagReturns$timeDifferenceMin <- as.numeric(TagReturns$timeDifferenceMin)
TagReturns$timeDifferenceMax <- as.numeric(TagReturns$timeDifferenceMax)
TagReturns$timeDifference <- as.numeric(TagReturns$timeDifference)

# Not sure why stat = "count" needs to be in there but causes the histogram to run so...
print(ggplot(data = TagReturns, (aes(category, fill = AvgtimeDifference))) + 
        geom_histogram(binwidth=1, colour = "white", stat = "count") + 
        theme(panel.background = element_rect(fill = "white", colour = "grey50")) + 
        labs(x = "Category", y="Count"))

TagReturns = TagReturns %>%
  group_by(timeDifference) %>%
  mutate(No.ofSameNumberOfDays = length(timeDifference)) %>%
  mutate_if(is.numeric, format, digits = 2)


Table <- TagReturns %>% 
  dplyr::select(category,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)

 Table1 <- unique(Table) %>%
             arrange(timeDifference)

kbl(Table1, col.names=c("Category", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
  kable_paper("striped", full_width = F)

Table1 %>% write.csv(paste0("C:/Users/", Sys.info()[7],"/Documents/GitHub/HerringScience.github.io/Source Data/Tag Returns/tagReturnsTracey.csv"))
```

## Tag Returns Scots Bay to German Bank, and German Bank to Scots Bay

```{r pressure, echo=FALSE}
TagReturnsSubset <- TagReturns[sample(1:nrow(TagReturns), 100, replace = FALSE),]

GBtoSB <- subset(TagReturns, subset = (FishingGround == "Scots Bay" & catchAREA == "German Bank" |
                                       FishingGround == "German Bank" & catchAREA == "Scots Bay" |
                                       FishingGround == "Scots Bay" & catchAREA == "German Bank (Area 7)" |
                                      FishingGround == "German" & TagReturns$catchAREA == "Scots (Area 8)" ))

GBtoSB$TagLocation <- with(GBtoSB, ifelse(GBtoSB$FishingGround == "Scots Bay", "SB to GB",
                                          ifelse(GBtoSB$FishingGround == "German Bank", "GB to SB","Other")))

GBtoSB$Count = 1


ggplot(GBtoSB, aes(x=TagLocation, y = Count, fill = factor(timeDifference))) +
        geom_bar(stat="identity") +
        labs(y = "Number of Events", x = "Initial Tag Location") +
        ggtitle("Tag Returns that started in either Scots Bay or German Bank, and were returned to the opposite ground") +
        labs(fill = "Days between tagging event and tag return")


Table <- GBtoSB %>% 
  dplyr::select(TAG_NUMBER,
                category,
                Date,
                FishingGround,
                DATE,
                catchAREA,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)


kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
  kable_paper("striped", full_width = F)

```
## All Tag returns associated with tagging events that started in either German Bank or Scots Bay

```{r pressure, echo=FALSE}

TagReturns$TagLocation <- with(TagReturns, ifelse(TagReturns$FishingGround == "Scots Bay" & TagReturns$catchAREA == "German Bank" |
                                                  TagReturns$FishingGround == "Scots Bay" & TagReturns$catchAREA == "German Bank (Area 7)"  , "SB to GB",
                                          ifelse(TagReturns$FishingGround == "German Bank" & TagReturns$catchAREA == "Scots Bay" |
                                                   TagReturns$FishingGround == "German Bank" & TagReturns$catchAREA == "Scots Bay (Area 8)", "GB to SB",
                                                 ifelse(TagReturns$FishingGround == "German Bank" & TagReturns$catchAREA == "German Bank", "GB to GB",
                                                        ifelse(TagReturns$FishingGround == "Scots Bay" & TagReturns$catchAREA == "Scots Bay", "SB to SB",
                                                               ifelse(TagReturns$FishingGround == "Scots Bay" & TagReturns$catchAREA != "Scots Bay" | 
                                                               TagReturns$FishingGround == "Scots Bay" & TagReturns$catchAREA != "German Bank", "SB to Other",
                                                               ifelse(TagReturns$FishingGround == "German Bank" & TagReturns$catchAREA != "Scots Bay" |
                                                                      TagReturns$FishingGround == "German Bank" & TagReturns$catchAREA != "German Bank", "GB to Other", "Other")))))))

TagReturns$Count <- 1

ggplot(TagReturns, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Tag Returns") +
  labs(fill = "Category")

Table <- TagReturns %>% 
  dplyr::select(TAG_NUMBER,
                category,
                Date,
                FishingGround,
                DATE,
                catchAREA,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)


kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
  kable_paper("striped", full_width = F)


```

## Tag Returns from German Bank Tagging Events

```{r pressure, echo=FALSE}
TagReturnsGB <- subset(TagReturns, subset = (FishingGround == "German Bank"))

TagReturnsGB$TagLocation <- with(TagReturnsGB, ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "German Bank" |
                                                      TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "German Bank (Area 7)", "GB to GB",
                                                  ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Scots Bay" |
                                                         TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Scots Bay (Area 8)", "GB to SB",
                                                         ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "NB Coastal", "GB to NBC",
                                                                ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Grand Manan", "GB to GM",
                                                                       ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Grand Manan Banks", "GB to GMB",
                                                                              ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Long Island", "GB and LI",
                                                                                            ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Seal Island", "GB and SI",
                                                                                                   ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Yankee Bank", "GB and YB",
                                                                                                          ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Trinity", "GB and T",
                                                                                                                 ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Browns Bank", "GB and BB",
                                                                                                                        ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "SW Grounds", "GB and SWG",
                                                                                                                               ifelse(TagReturnsGB$FishingGround == "German Bank" & TagReturnsGB$catchAREA == "Gannet Dry Ledge", "GB and GDL",
                                                                                                                                      ifelse(TagReturnsSWG$FishingGround == "German Bank" & TagReturnsSWG$catchAREA == "Lurcher", "GB and L","Other"
                                                                                                                                      ))))))))))))))



ggplot(TagReturnsGB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("German Bank Tag Returns") +
  labs(fill = "Category")

Table <- TagReturnsGB %>% 
  dplyr::select(TAG_NUMBER,
                category,
                Date,
                FishingGround,
                DATE,
                catchAREA,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)


kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
  kable_paper("striped", full_width = F)

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsGB <- subset(TagReturnsGB, subset = (category != "1"))

ggplot(TagReturnsGB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("German Bank Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")

Table <- TagReturnsGB %>% 
  dplyr::select(TAG_NUMBER,
                category,
                Date,
                FishingGround,
                DATE,
                catchAREA,
                timeDifference,
                AvgtimeDifference,
                timeDifferenceMin,
                timeDifferenceMax,
                No.InCategory,
                No.ofSameNumberOfDays)


kbl(Table, col.names=c("Tag Number", "Category", "Tagged Date", "Tagged Ground", "Catch Date", "Catch Area", "Time Difference (days)", "Average Time Difference (days)", "Minimum Time Difference", "Maximum Time Difference", "Amount in the Same Category", "Amount with the same number of Days"), align = "c") %>%
  kable_paper("striped", full_width = F)

```
## Tag Returns from NB Coastal Tagging Events
```{r pressure, echo=FALSE}

#NB Coastal
TagReturnsNBC <- subset(TagReturns, subset = (FishingGround == "NB Coastal"))

TagReturnsNBC$TagLocation <- with(TagReturnsNBC, ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "German Bank" |
                                                        TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "German Bank (Area 7)", "NBC to GB",
                                                      ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Scots Bay" |
                                                             TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Scots Bay (Area 8)", "NBC to SB",
                                                             ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "NB Coastal", "NBC to NBC",
                                                                    ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Grand Manan", "NBC to GM",
                                                                           ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Grand Manan Banks", "NBC to GMB",
                                                                                  ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Long Island", "NBC and LI",
                                                                                                ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Seal Island", "NBC and SI",
                                                                                                       ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Yankee Bank", "NBC and YB",
                                                                                                              ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Trinity", "NBC and T",
                                                                                                                     ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Browns Bank", "NBC and BB",
                                                                                                                            ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "SW Grounds", "NBC and SWG",
                                                                                                                                   ifelse(TagReturnsNBC$FishingGround == "NB Coastal" & TagReturnsNBC$catchAREA == "Gannet Dry Ledge", "NBC and GDL",
                                                                                                                                          ifelse(TagReturnsSWG$FishingGround == "NB Coastal" & TagReturnsSWG$catchAREA == "Lurcher", "NBC and L","Other"
                                                                                                                                   ))))))))))))))

ggplot(TagReturnsNBC, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("NB Coastal Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsNBC <- subset(TagReturnsNBC, subset = (category != "1"))

ggplot(TagReturnsNBC, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("NB Coastal Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")

```

#Grand Manan
```{r pressure, echo=FALSE}

TagReturnsGM <- subset(TagReturns, subset = (FishingGround == "Grand Manan"))

TagReturnsGM$TagLocation <- with(TagReturnsGM, ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "German Bank" |
                                                          TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "German Bank (Area 7)", "GM to GB",
                                                        ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Scots Bay" |
                                                                 TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Scots Bay (Area 8)", "GM to SB",
                                                               ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "NB Coastal", "GM to NBC",
                                                                      ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Grand Manan", "GM to GM",
                                                                             ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Grand Manan Banks", "GM to GMB",
                                                                                    ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Long Island", "GM and LI",
                                                                                                  ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Seal Island", "GM and SI",
                                                                                                         ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Yankee Bank", "GM and YB",
                                                                                                                ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Trinity", "GM and T",
                                                                                                                       ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Browns Bank", "GM and BB",
                                                                                                                              ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "SW Grounds", "GM and SWG",
                                                                                                                                     ifelse(TagReturnsGM$FishingGround == "Grand Manan" & TagReturnsGM$catchAREA == "Gannet Dry Ledge", "GM and GDL",
                                                                                                                                            ifelse(TagReturnsSWG$FishingGround == "Grand Manan" & TagReturnsSWG$catchAREA == "Lurcher", "GM and L", "Other"
                                                                                                                                     ))))))))))))))

ggplot(TagReturnsGM, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Grand Manan Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsGM <- subset(TagReturnsGM, subset = (category != "1"))

ggplot(TagReturnsGM, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Grand Manan Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")

```

#Grand Manan Banks
```{r pressure, echo=FALSE}

TagReturnsGMB <- subset(TagReturns, subset = (FishingGround == "Grand Manan Banks"))

TagReturnsGMB$TagLocation <- with(TagReturnsGMB, ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "German Bank" |
                                                        TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "German Bank (Area 7)", "GMB to GB",
                                                      ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Scots Bay" |
                                                               TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Scots Bay (Area 8)", "GMB to SB",
                                                             ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "NB Coastal", "GMB to NBC",
                                                                    ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Grand Manan", "GMB to GM",
                                                                           ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Grand Manan Banks", "GMB to GMB",
                                                                                  ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Long Island", "GMB and LI",
                                                                                                ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Seal Island", "GMB and SI",
                                                                                                       ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Yankee Bank", "GMB and YB",
                                                                                                              ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Trinity", "GMB and T",
                                                                                                                     ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Browns Bank", "GMB and BB",
                                                                                                                            ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "SW Grounds", "GMB and SWG",
                                                                                                                                   ifelse(TagReturnsGMB$FishingGround == "Grand Manan Banks" & TagReturnsGMB$catchAREA == "Gannet Dry Ledge", "GMB and GDL",
                                                                                                                                          ifelse(TagReturnsSWG$FishingGround == "Grand Manan Banks" & TagReturnsSWG$catchAREA == "Lurcher", "GMB and L","Other"
                                                                                                                                   ))))))))))))))

ggplot(TagReturnsGMB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Grand Manan Banks Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsGMB <- subset(TagReturnsGMB, subset = (category != "1"))

ggplot(TagReturnsGMB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Grand Manan Banks Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")

```

#Long Island
```{r pressure, echo=FALSE}
TagReturnsLI <- subset(TagReturns, subset = (FishingGround == "Long Island"))

TagReturnsLI$TagLocation <- with(TagReturnsLI, ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "German Bank" |
                                                          TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "German Bank (Area 7)", "LI to GB",
                                                        ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Scots Bay" |
                                                                 TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Scots Bay (Area 8)", "LI to SB",
                                                               ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "NB Coastal", "LI to NBC",
                                                                      ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Grand Manan", "LI to GM",
                                                                             ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Grand Manan Banks", "LI to GMB",
                                                                                    ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Long Island", "LI and LI",
                                                                                                  ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Seal Island", "LI and SI",
                                                                                                         ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Yankee Bank", "LI and YB",
                                                                                                                ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Trinity", "LI and T",
                                                                                                                       ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Browns Bank", "LI and BB",
                                                                                                                              ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "SW Grounds", "LI and SWG",
                                                                                                                                     ifelse(TagReturnsLI$FishingGround == "Long Island" & TagReturnsLI$catchAREA == "Gannet Dry Ledge", "LI and GDL",
                                                                                                                                            ifelse(TagReturnsSWG$FishingGround == "Long Island" & TagReturnsSWG$catchAREA == "Lurcher", "LI and L","Other"
                                                                                                                                     ))))))))))))))

ggplot(TagReturnsLI, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Long Island Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsLI <- subset(TagReturnsLI, subset = (category != "1"))

ggplot(TagReturnsLI, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Long Island Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#Seal Island 
```{r pressure, echo=FALSE}
TagReturnsSI <- subset(TagReturns, subset = (FishingGround == "Seal Island"))

TagReturnsSI$TagLocation <- with(TagReturnsSI, ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "German Bank" |
                                                        TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "German Bank (Area 7)", "SI to GB",
                                                      ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Scots Bay" |
                                                               TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Scots Bay (Area 8)", "SI to SB",
                                                             ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "NB Coastal", "SI to NBC",
                                                                    ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Grand Manan", "SI to GM",
                                                                           ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Grand Manan Banks", "SI to GMB",
                                                                                  ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Long Island", "SI and LI",
                                                                                                ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Seal Island", "SI and SI",
                                                                                                       ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Yankee Bank", "SI and YB",
                                                                                                              ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Trinity", "SI and T",
                                                                                                                     ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Browns Bank", "SI and BB",
                                                                                                                            ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "SW Grounds", "SI and SWG",
                                                                                                                                   ifelse(TagReturnsSI$FishingGround == "Seal Island" & TagReturnsSI$catchAREA == "Gannet Dry Ledge", "SI and GDL",
                                                                                                                                          ifelse(TagReturnsSWG$FishingGround == "Seal Island" & TagReturnsSWG$catchAREA == "Lurcher", "SI and L", "Other"
                                                                                                                                   ))))))))))))))

ggplot(TagReturnsSI, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Seal Island Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsSI <- subset(TagReturnsSI, subset = (category != "1"))

ggplot(TagReturnsSI, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Seal Island Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#Scots Bay

```{r pressure, echo=FALSE}
TagReturnsSB <- subset(TagReturns, subset = (FishingGround == "Scots Bay"))

TagReturnsSB$TagLocation <- with(TagReturnsSB, ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "German Bank" |
                                                        TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "German Bank (Area 7)", "SB to GB",
                                                      ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Scots Bay" |
                                                               TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Scots Bay (Area 8)", "SB to SB",
                                                             ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "NB Coastal", "SB to NBC",
                                                                    ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Grand Manan", "SB to GM",
                                                                           ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Grand Manan Banks", "SB to GMB",
                                                                                  ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Long Island", "SB and LI",
                                                                                         ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Seal Island", "SB and SI",
                                                                                                ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Yankee Bank", "SB and YB",
                                                                                                       ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Trinity", "SB and T",
                                                                                                              ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Browns Bank", "SB and BB",
                                                                                                                     ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "SW Grounds", "SB and SWG",
                                                                                                                            ifelse(TagReturnsSB$FishingGround == "Scots Bay" & TagReturnsSB$catchAREA == "Gannet Dry Ledge", "SB and GDL",
                                                                                                                                   ifelse(TagReturnsSWG$FishingGround == "Scots Bay" & TagReturnsSWG$catchAREA == "Lurcher", "SB and L","Other"
                                                                                                                            ))))))))))))))

ggplot(TagReturnsSB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Scots Bay Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsSB <- subset(TagReturnsSB, subset = (category != "1"))

ggplot(TagReturnsSB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Scots Bay Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#Yankee Bank

```{r pressure, echo=FALSE}
TagReturnsYB <- subset(TagReturns, subset = (FishingGround == "Yankee Bank"))

TagReturnsYB$TagLocation <- with(TagReturnsYB, ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "German Bank" |
                                                        TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "German Bank (Area 7)", "YB to GB",
                                                      ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Scots Bay" |
                                                               TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Scots Bay (Area 8)", "YB to SB",
                                                             ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "NB Coastal", "YB to NBC",
                                                                    ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Grand Manan", "YB to GM",
                                                                           ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Grand Manan Banks", "YB to GMB",
                                                                                  ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Long Island", "YB and LI",
                                                                                         ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Seal Island", "YB and SI",
                                                                                                ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Yankee Bank", "YB and YB",
                                                                                                       ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Trinity", "YB and T",
                                                                                                              ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Browns Bank", "YB and BB",
                                                                                                                     ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "SW Grounds", "YB and SWG",
                                                                                                                            ifelse(TagReturnsYB$FishingGround == "Yankee Bank" & TagReturnsYB$catchAREA == "Gannet Dry Ledge", "YB and GDL",
                                                                                                                                   ifelse(TagReturnsSWG$FishingGround == "Yankee Bank" & TagReturnsSWG$catchAREA == "Lurcher", "YB and L", "Other"
                                                                                                                            ))))))))))))))

ggplot(TagReturnsYB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Yankee Bank Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsYB <- subset(TagReturnsYB, subset = (category != "1"))

ggplot(TagReturnsYB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Yankee Bank Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#Trinity

```{r pressure, echo=FALSE}
TagReturnsT <- subset(TagReturns, subset = (FishingGround == "Trinity"))

TagReturnsT$TagLocation <- with(TagReturnsT, ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "German Bank" |
                                                        TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "German Bank (Area 7)", "T to GB",
                                                      ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Scots Bay" |
                                                               TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Scots Bay (Area 8)", "T to SB",
                                                             ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "NB Coastal", "T to NBC",
                                                                    ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Grand Manan", "T to GM",
                                                                           ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Grand Manan Banks", "T to GMB",
                                                                                  ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Long Island", "T and LI",
                                                                                         ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Seal Island", "T and SI",
                                                                                                ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Yank", "T and YB",
                                                                                                       ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Trinity", "T and T",
                                                                                                              ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Browns Bank", "T and BB",
                                                                                                                     ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "SW Grounds", "T and SWG",
                                                                                                                            ifelse(TagReturnsT$FishingGround == "Trinity" & TagReturnsT$catchAREA == "Gannet Dry Ledge", "T and GDL",
                                                                                                                                   ifelse(TagReturnsSWG$FishingGround == "Trinity" & TagReturnsSWG$catchAREA == "Lurcher", "T and L","Other"
                                                                                                                            ))))))))))))))

ggplot(TagReturnsT, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Trinity Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsT <- subset(TagReturnsT, subset = (category != "1"))

ggplot(TagReturnsT, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Trinity Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#Browns Bank

```{r pressure, echo=FALSE}
TagReturnsBB <- subset(TagReturns, subset = (FishingGround == "Browns Bank"))

TagReturnsBB$TagLocation <- with(TagReturnsBB, ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "German Bank" |
                                                      TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "German Bank (Area 7)", "BB to GB",
                                                    ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Scots Bay" |
                                                             TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Scots Bay (Area 8)", "BB to SB",
                                                           ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "NB Coastal", "BB to NBC",
                                                                  ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Grand Manan", "BB to GM",
                                                                         ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Grand Manan Banks", "BB to GMB",
                                                                                ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Long Island", "BB and LI",
                                                                                       ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Seal Island", "BB and SI",
                                                                                              ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Yank", "BB and YB",
                                                                                                     ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Trinity", "BB and T",
                                                                                                            ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Browns Bank", "BB and BB",
                                                                                                                   ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "SW Grounds", "BB and SWG",
                                                                                                                          ifelse(TagReturnsBB$FishingGround == "Browns Bank" & TagReturnsBB$catchAREA == "Gannet Dry Ledge", "BB and GDL",
                                                                                                                                 ifelse(TagReturnsSWG$FishingGround == "Browns Bank" & TagReturnsSWG$catchAREA == "Lurcher", "BB and L", "Other"
                                                                                                                          ))))))))))))))

ggplot(TagReturnsBB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Browns Bank Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsBB <- subset(TagReturnsBB, subset = (category != "1"))

ggplot(TagReturnsBB, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Browns Bank Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#SW Ground

```{r pressure, echo=FALSE}
TagReturnsSWG <- subset(TagReturns, subset = (FishingGround == "SW Grounds"))

TagReturnsSWG$TagLocation <- with(TagReturnsSWG, ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "German Bank" |
                                                        TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "German Bank (Area 7)", "SWG to GB",
                                                      ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Scots Bay" |
                                                               TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Scots Bay (Area 8)", "SWG to SB",
                                                             ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "NB Coastal", "SWG to NBC",
                                                                    ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Grand Manan", "SWG to GM",
                                                                           ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Grand Manan Banks", "SWG to GMB",
                                                                                  ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Long Island", "SWG and LI",
                                                                                         ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Seal Island", "SWG and SI",
                                                                                                ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Yank", "SWG and YB",
                                                                                                       ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Trinity", "SWG and T",
                                                                                                              ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Browns Bank", "SWG and BB",
                                                                                                                     ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "SW Grounds", "SWG and SWG",
                                                                                                                            ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Gannet Dry Ledge", "SWG and GDL",
                                                                                                                                   ifelse(TagReturnsSWG$FishingGround == "SW Grounds" & TagReturnsSWG$catchAREA == "Lurcher", "GDL and L", 
                                                                                                                                          "Other"
                                                                                                                            ))))))))))))))

ggplot(TagReturnsSWG, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("SW Grounds Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsSWG <- subset(TagReturnsSWG, subset = (category != "1"))

ggplot(TagReturnsSWG, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("SW Grounds Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")

```

#Gannet Dry Ledge

```{r pressure, echo=FALSE}
TagReturnsGDL <- subset(TagReturns, subset = (FishingGround == "Gannet Dry Ledge"))

TagReturnsGDL$TagLocation <- with(TagReturnsGDL, ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "German Bank" |
                                                          TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "German Bank (Area 7)", "GDL to GB",
                                                        ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Scots Bay" |
                                                                 TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Scots Bay (Area 8)", "GDL to SB",
                                                               ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "NB Coastal", "GDL to NBC",
                                                                      ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Grand Manan", "GDL to GM",
                                                                             ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Grand Manan Banks", "GDL to GMB",
                                                                                    ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Long Island", "GDL and LI",
                                                                                           ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Seal Island", "GDL and SI",
                                                                                                  ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Yank", "GDL and YB",
                                                                                                         ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Trinity", "GDL and T",
                                                                                                                ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Browns Bank", "GDL and BB",
                                                                                                                       ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "SW Grounds", "GDL and SWG",
                                                                                                                              ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Gannet Dry Ledge", "GDL and GDL",
                                                                                                                                     ifelse(TagReturnsGDL$FishingGround == "Gannet Dry Ledge" & TagReturnsGDL$catchAREA == "Lurcher", "GDL and L","Other"
                                                                                                                              ))))))))))))))

ggplot(TagReturnsGDL, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Gannet Dry Ledge Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsGDL <- subset(TagReturnsGDL, subset = (category != "1"))

ggplot(TagReturnsGDL, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Gannet Dry Ledge Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Category")
```

#Lurcher

```{r pressure, echo=FALSE}
TagReturnsL <- subset(TagReturns, subset = (FishingGround == "Lurcher"))

TagReturnsL$TagLocation <- with(TagReturnsL, ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "German Bank" |
                                                          TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "German Bank (Area 7)", "L to GB",
                                                        ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Scots Bay" |
                                                                 TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Scots Bay (Area 8)", "L to SB",
                                                               ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "NB Coastal", "L to NBC",
                                                                      ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Grand Manan", "L to GM",
                                                                             ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Grand Manan Banks", "L to GMB",
                                                                                    ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Long Island", "L and LI",
                                                                                           ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Seal Island", "L and SI",
                                                                                                  ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Yank", "L and YB",
                                                                                                         ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Trinity", "L and T",
                                                                                                                ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Browns Bank", "L and BB",
                                                                                                                       ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "SW Grounds", "L and SWG",
                                                                                                                              ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Gannet Dry Ledge", "L and GDL",
                                                                                                                                     ifelse(TagReturnsL$FishingGround == "Lurcher" & TagReturnsL$catchAREA == "Lurcher", "L and Lurcher", "Other"
                                                                                                                              ))))))))))))))

ggplot(TagReturnsL, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Lurcher Tag Returns") +
  labs(fill = "Category")

#Removed category 1 larvae - any caught within 2 days of tagging.

TagReturnsL <- subset(TagReturnsL, subset = (category != "1"))

ggplot(TagReturnsL, aes(x=TagLocation, y = Count, fill = factor(category))) +
  geom_bar(stat="identity") +
  labs(y = "Number of Events", x = "Tag to Catch Location") +
  ggtitle("Lurcher Tag Returns excluding fish caught within 2 days of being tagged") +
  labs(fill = "Categor")

```


